### 2016-02-10 submission.tex
Added article skeleton

%
% File naaclhlt2016.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2016}
\usepackage{times}
\usepackage{latexsym}

%\naaclfinalcopy % Uncomment this line for the final submission
\def\naaclpaperid{***} %  Enter the naacl Paper ID here

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}

%todo: possibly a title that reflects the work better? 
\title{Detecting threats of violence in online discussions}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Author 1\\
	    XYZ Company\\
	    111 Anywhere Street\\
	    Mytown, NY 10000, USA\\
	    {\tt author1@xyz.org}
	  \And
	Author 2\\
  	ABC University\\
  	900 Main Street\\
  	Ourcity, PQ, Canada A1A 1T2\\
  {\tt author2@abc.ca}}

\date{}

\begin{document}

\maketitle

\begin{abstract}
Here comes an abstract for this article
\end{abstract}

\section{Introduction}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
big scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

In this article, we \ldots

\section{Previous work}

\section{Data set}

\section{Experiments}

\subsection{Experimental setup}

\subsection{Results}

%\subsection{Error analysis}

%\subsection{Held-out results}

\section{Discussion}

\bibliography{wassa2016}
\bibliographystyle{naaclhlt2016}

\end{document}

### 2016-02-10 submission.tex
Added some text to intro and data set

@@
 
+\usepackage{verbatim}
+\usepackage{booktabs}
+
 %\naaclfinalcopy % Uncomment this line for the final submission
 \def\naaclpaperid{***} %  Enter the naacl Paper ID here
+
+\newcommand{\tov}{threat of violence}
+\newcommand{\Tov}{Threat of violence}
+\newcommand{\tovs}{threats of violence}
+\newcommand{\Tovs}{Threats of violence}
+\newcommand{\hugo}{Hugo Lewi Hammer}
+\newcommand{\Dep}{Dependency parsing}
+\newcommand{\dep}{dependency parsing}
+
+\newcommand{\Ds}{The YouTube threat data set}
+\newcommand{\ds}{the YouTube threat data set}
 
@@
 \section{Introduction}
+\label{sec:intro}
 Threats of violence is an increasingly common occurrence in online
@@
 \section{Previous work}
+\label{sec:prev}
+There is little previous work specifically devoted to the detection of
+threats of violence in text, however, there is previous work which
+examines other types of closely related phenomena, such as
+cyberbullying and hate-speech.
 
-\section{Data set}
+\section{The YouTube threat data set}
+\label{sec:data}
+The YouTube threat data set is comprised of user-written comments from
+eight different YouTube videos \cite{hammer2014}. A comment
+consists of a set of sentences, each of them manually annotated to be
+either a \tov{} (or support for a \tov{}) or not. The data set
+furthermore records the username\footnote{In 2013, YouTube changed its
+  commenting system from using unique usernames, to using "real
+  names", like Facebook and other sites \cite{youtube2013}. Some
+  accounts, however, did not provide real names, so they continue to
+  only be identified by their usernames.} of the user that posted the
+comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
+Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
+%The videos cover slightly different topics, the videos all contain the same
+%type of discussions, namely of xenophobia and racism.
+
+The \ds consists of 9,845 comments, comprised of 28,643
+sentences, see table \ref{tab:dataset}. In total there are 402,673 tokens in the sentences in the
+data set. There are 1,285 comments containing threats, and 1,384
+sentences containing threats, as seen in table \ref{tab:dataset}.
+\cite{hammer2014} report inter annotator agreement on this data
+set to be 98~\%, as calculated on 120 of the comments, doubly
+annotated for evaluation.
+
+Figure \ref{fig:comments} contains examples of some comments containing
+\tovs{} taken from the data set. The first line is the username or
+name, and the subsequent lines are the sentences of the comment. An
+empty line indicates the end of a comment. The sentences are annotated
+with a number indicating whether they contain a \tov{} (1), or not
+(0).
+
+\begin{figure}[h]
+\begin{verbatim}
+timpa666
+1    and i will kill every fucking muslim and arab!
+
+NimsXdimensions
+0    Need a solution?
+1    Drop one good ol' nuke on that black toilet in Mecca.
+
+Ammar Alozaibi
+1    Funny, We will conquer you all in just few years, U will be
+     my slave and your women will be my Sex Toy in Bed.
+
+LegitZombieSlayer1
+0     As long as i'm alive you'll have no victory.
+1     I'll kill all you cunts
+
+\end{verbatim}
+\caption{Examples of comments from the data set.}
+\label{fig:comments}
+\end{figure}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lrrr}
+  %&   &   &   \\
+  \toprule
+
+  & Commments  & Sentences  & Users posting \\
+  \midrule
+
+  Total  & $9,845$  & $28,643$  & $5,483$  \\
+  Threats  & $1,285$  & $1,384$  & $992$  \\
+  \bottomrule
+
+\end{tabular}
+\end{center}
+\caption{Number of comments, sentences and users in \ds{}}
+\label{tab:dataset}
+\end{table}
 
 \section{Experiments}
+\label{sec:exp}
 
@@
 \section{Discussion}
+\label{sec:disc}
 

### 2016-02-10 submission.tex
Added references

@@
 %todo: possibly a title that reflects the work better? 
-\title{Detecting threats of violence in online discussions}
+\title{Detecting threats of violence in YouTube comments}
 
@@
 discussions online. Moderators of social networks operate on such a
-big scale that manually reading all posts is an insurmountable
+large scale that manually reading all posts is an insurmountable
 task. Methods for automatically detecting threats could therefore
@@
 
-In this article, we \ldots
+In this article, we evaluate different types of features for the task
+of detecting threats of violence in YouTube comments. We show that ...
 
@@
 cyberbullying and hate-speech.
+
+\newcite{dinakar2011} proposes a method for the detection of
+cyberbullying by targeting combinations of profane or negative words,
+and words related to several predetermined sensitive topics. Their
+data set consists of over 50,000 YouTube comments taken from videos
+about controversial topics. The topics included sexuality, race,
+culture and intelligence. The comments were grouped by topic, and then
+12~\% of these were manually annotated to check that they were placed
+in the right category.
+
+The first stage of the detection was the same across all
+categories. It consisted of using a lexicon of negative words and a
+list of profane words, as well as part-of-speech tags from the
+training data that were correlated with bullying. The second stage was
+category-specific, and used commonly observed uni- and bigrams from
+each category as features. The experiments reported accuracies from
+63~\% to 80~\%, but did not report precision or recall.
 
@@
 
-The \ds consists of 9,845 comments, comprised of 28,643
-sentences, see table \ref{tab:dataset}. In total there are 402,673 tokens in the sentences in the
-data set. There are 1,285 comments containing threats, and 1,384
-sentences containing threats, as seen in table \ref{tab:dataset}.
-\cite{hammer2014} report inter annotator agreement on this data
-set to be 98~\%, as calculated on 120 of the comments, doubly
-annotated for evaluation.
-
-Figure \ref{fig:comments} contains examples of some comments containing
-\tovs{} taken from the data set. The first line is the username or
-name, and the subsequent lines are the sentences of the comment. An
-empty line indicates the end of a comment. The sentences are annotated
-with a number indicating whether they contain a \tov{} (1), or not
-(0).
-
-\begin{figure}[h]
-\begin{verbatim}
-timpa666
-1    and i will kill every fucking muslim and arab!
-
-NimsXdimensions
-0    Need a solution?
-1    Drop one good ol' nuke on that black toilet in Mecca.
-
-Ammar Alozaibi
-1    Funny, We will conquer you all in just few years, U will be
-     my slave and your women will be my Sex Toy in Bed.
-
-LegitZombieSlayer1
-0     As long as i'm alive you'll have no victory.
-1     I'll kill all you cunts
-
-\end{verbatim}
-\caption{Examples of comments from the data set.}
-\label{fig:comments}
-\end{figure}
+The data set consists of 9,845 comments, comprised of 28,643
+sentences, see table \ref{tab:dataset}. In total there are 402,673
+tokens in the sentences in the data set. There are 1,285 comments
+containing threats, and 1,384 sentences containing threats, as seen in
+table \ref{tab:dataset}.  \cite{hammer2014} report inter annotator
+agreement on this data set to be 98~\%, as calculated on 120 of the
+comments, doubly annotated for evaluation.
 
@@
 
+%to-do: should we anonymize the user names?
+Figure \ref{fig:comments} provides some examples of comments containing
+\tovs{} taken from the data set. The first line is the username or
+name, and the subsequent lines are the sentences of the comment. An
+empty line indicates the end of a comment. The sentences are annotated
+with a number indicating whether they contain a \tov{} (1), or not
+(0).
+
+\begin{figure}[h]
+\begin{verbatim}
+timpa666
+1    and i will kill every fucking muslim and arab!
+
+NimsXdimensions
+0    Need a solution?
+1    Drop one good ol' nuke on that black toilet in Mecca.
+
+Ammar Alozaibi
+1    Funny, We will conquer you all in just few years, U will be
+     my slave and your women will be my Sex Toy in Bed.
+
+\end{verbatim}
+\caption{Examples of comments from the data set.}
+\label{fig:comments}
+\end{figure}
+
 \section{Experiments}
@@
 \subsection{Experimental setup}
+%% todo:
+%% - data split
+%% - preprocessing
+%% - machine learner
+%% - tuning
+%% - feature templates
 

### 2016-02-10 submission.tex
More previous work

@@
 in the right category.
-
 The first stage of the detection was the same across all
@@
 63~\% to 80~\%, but did not report precision or recall.
+
+There has been quite a bit of work focused on the detection of threats
+in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
+The data set used for these experiments consisted a collection of 5000
+threatening tweets collected by a website over a period of about two
+years. In addition, a large number of random tweets were collected for
+development and testing. A set of 2.3 million random tweets was used
+for development, and a set of 1 million was used for testing. This set
+was not annotated in any way prior to being used in the experiments.
+The system relies on manually constructed recognition patterns, in the
+form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
+trigrams), but do not go into detail about the methods used to
+construct these patterns, stating that the researchers relied on their
+(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
+\newcite{nellshallow2013}, a manually crafted shallow parser is added
+to the system. This improves results to a precision of 39\% and a
+recall of 59\%.
+
+\newcite{warner2012} present a method for detecting unwanted or
+illegal comments in user-generated web text from the internet, which
+relies on machine learning in combination with template-based
+features. The data set used in the research came from two sources. The
+first consists of posts from Yahoo news groups, the second were
+webpages collected by the American Jewish Congress that had been
+identified as offensive. The data set was manually annotated, and then
+the hate speech was assigned to a category, such as antisemitic,
+anti-woman, anti-asian, etc. The research then focused on the
+antisemitic category.  The research approaches the problem as a
+word-sense disambiguation task, since the same words can be used in
+both hateful and non-hateful contexts. The features used in the
+classification were combinations of uni-, bi- and trigrams,
+part-of-speech-tags and Brown clusters.  The best results of the
+classifications were obtained using only unigrams as features, with a
+precision of 67~\% and a recall of 60~\%. The other feature sets
+garnered much lower results, and the authors suggest that deeper
+parsing could reveal significant phrase patterns.
 
@@
 
-\begin{figure}[h]
+\begin{figure*}[h]
 \begin{verbatim}
@@
 \label{fig:comments}
-\end{figure}
+\end{figure*}
 

### 2016-02-15 submission.tex
Added experimental setup

@@
 \usepackage{booktabs}
+
+\usepackage{pgfplots}
+% Anbefalt her: https://www.sharelatex.com/learn/Pgfplots_package#Introduction
+\pgfplotsset{width=10cm}
 
@@
 \label{sec:intro}
-Threats of violence is an increasingly common occurrence in online
+Threats of violence constitute an increasingly common occurrence in online
 discussions. It disproportionally affects women and minorities, often
@@
 containing threats, and 1,384 sentences containing threats, as seen in
-table \ref{tab:dataset}.  \cite{hammer2014} report inter annotator
+table \ref{tab:dataset}.  \newcite{hammer2014} report inter annotator
 agreement on this data set to be 98~\%, as calculated on 120 of the
@@
 
-\begin{figure*}[h]
+\begin{figure*}
 \begin{verbatim}
@@
 \subsection{Experimental setup}
+The data set is split into an 80-20 training and testing set. All
+tuning and development experiments were performed using 10-fold
+cross-validation on the training set.
+
+Since threat annotation is performed on the sentence level, the data
+set has been manually split into sentences as part of the annotation
+process.  We performed tokenization, lemmatization, PoS-tagging and
+dependency parsing using the spaCy toolkit REF.  SpaCy assigns both
+the standard Penn Treebank PoS-tags REF, as well as the more
+coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
+dependency parser assigns an analysis in compliance with the ClearNLP
+converter REF. The data set was further enriched with the cluster
+labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created
+using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced
+from the RCV1 corpus, a corpus containing Reuters English newswire
+text, with approximately 63 million words and 3.3 million sentences.
+WordNet REF
+
 %% todo:
@@
 %% - preprocessing
+%%   Spacy, Brown clusters, WordNet
 %% - machine learner
@@
 
-%\subsection{Error analysis}
+\subsection{Error analysis}
 
-%\subsection{Held-out results}
+\subsection{Held-out results}
 
-\section{Discussion}
+\section{Conclusion}
 \label{sec:disc}

### 2016-02-17 submission.tex
Added experimental setup

@@
 \usepackage{latexsym}
+\usepackage{relsize}
 
@@
 
-\usepackage{pgfplots}
-% Anbefalt her: https://www.sharelatex.com/learn/Pgfplots_package#Introduction
-\pgfplotsset{width=10cm}
+\usepackage{tikz-qtree}
+\usepackage{tikz-dependency}
 
@@
 \newcommand{\ds}{the YouTube threat data set}
+
+\let\tag=\textsc
 
@@
 In this article, we evaluate different types of features for the task
-of detecting threats of violence in YouTube comments. We show that ...
+of detecting threats of violence in YouTube comments. We draw on both
+lexical, morphosyntactic and lexical semantic information sources and
+experiment with different machine learning algorithms. Our results
+indicate that successful detection of threats of violence is largely
+determined by lexical information.
 
@@
 data set consists of over 50,000 YouTube comments taken from videos
-about controversial topics. The topics included sexuality, race,
-culture and intelligence. The comments were grouped by topic, and then
-12~\% of these were manually annotated to check that they were placed
-in the right category.
-The first stage of the detection was the same across all
-categories. It consisted of using a lexicon of negative words and a
-list of profane words, as well as part-of-speech tags from the
-training data that were correlated with bullying. The second stage was
-category-specific, and used commonly observed uni- and bigrams from
-each category as features. The experiments reported accuracies from
-63~\% to 80~\%, but did not report precision or recall.
+about controversial topics. They adopt a two-stage approach, where the
+first stage consists of using a lexicon of negative words and a list
+of profane words, as well as part-of-speech tags from the training
+data that were correlated with bullying. The second stage is
+category-specific, and makes use of commonly observed uni- and bigrams
+from each category as features. The experiments reported accuracies
+from 63~\% to 80~\%, but did not report precision or recall.
+% lists of negative and profane words
+% correlated words from training data
 
@@
 in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
-The data set used for these experiments consisted a collection of 5000
+The data set used for these experiments consists of a collection of 5000
 threatening tweets collected by a website over a period of about two
@@
 development and testing. A set of 2.3 million random tweets was used
-for development, and a set of 1 million was used for testing. This set
-was not annotated in any way prior to being used in the experiments.
+for development, and a set of 1 million was used for testing. 
 The system relies on manually constructed recognition patterns, in the
@@
 to the system. This improves results to a precision of 39\% and a
-recall of 59\%.
+recall of 59\% \footnote{Perhaps a footnote on the peculiarities of the evaluation??}.
+% handcrafted patterns
+% rule-based shallow parser
+% dubious evaluation
 
@@
 identified as offensive. The data set was manually annotated, and then
-the hate speech was assigned to a category, such as antisemitic,
-anti-woman, anti-asian, etc. The research then focused on the
-antisemitic category.  The research approaches the problem as a
+the hate speech was assigned to a category, such as anti-Semitic,
+anti-woman, anti-Asian, etc. The task is then approached as a
 word-sense disambiguation task, since the same words can be used in
@@
 parsing could reveal significant phrase patterns.
+% only unigrams best results
+% suggests parsing might help
+
+\newcite{hammer2014} reports an experiment on the data set that we
+will be using in our own experiments, although it has been changed
+slightly since the publication of his initial study. The method used a
+logistic LASSO regression analysis on bigrams (skip-grams) of
+important words to classify sentences as \tovs{} or not.
+The method described in the article uses a set of important words that
+are correlated with threats of violence. The features are bigrams of
+two of these important words observed in the same sentence. The
+article does not describe exactly how these important words were
+selected, stating only that words were chosen that were significantly
+correlated with the response (violent/non-violent sentence).
+Results are reported only in terms of proportion of false positives for the two classes and it is not clear how the data was split for training and evaluation.
 
@@
 \label{sec:exp}
+Much of the previous work in Section \ref{sec:prev} made use of
+precompiled lists of correlated words and manually crafted
+patterns. Whereas these resources can be effective, they are highly
+task-specific and do not easily lend themselves to replication.  The
+previous work further highlights the effectiveness of lexical features
+(words-based features), however, several of the authors suggest that parsing
+may be beneficial for these tasks.
+
+In this work we experiment with a wide range of linguistic information
+as features in our system and investigate the introduction of
+linguistic context through a set of feature templates. We also
+generalize these features through a backoff technique. Throughout, we
+make use of freely available, re-usable resources and tools in order
+to construct our system.
 
 \subsection{Experimental setup}
-The data set is split into an 80-20 training and testing set. All
-tuning and development experiments were performed using 10-fold
-cross-validation on the training set.
 
-Since threat annotation is performed on the sentence level, the data
+\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the data
 set has been manually split into sentences as part of the annotation
 process.  We performed tokenization, lemmatization, PoS-tagging and
-dependency parsing using the spaCy toolkit REF.  SpaCy assigns both
-the standard Penn Treebank PoS-tags REF, as well as the more
+dependency parsing using the SpaCy
+toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard
+Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more
 coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
 dependency parser assigns an analysis in compliance with the ClearNLP
-converter REF. The data set was further enriched with the cluster
-labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created
-using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced
-from the RCV1 corpus, a corpus containing Reuters English newswire
-text, with approximately 63 million words and 3.3 million sentences.
+converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example
+dependency graph from the data set. The data set was further enriched
+with the cluster labels described in Turian et
+al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering
+algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
+corpus containing Reuters English newswire text, with approximately 63
+million words and 3.3 million sentences. We vary the number of clusters to be either 100,
+320, 1000 or 3200 clusters and use the full cluster label.
  WordNet REF
 
-%% todo:
-%% - data split
-%% - preprocessing
-%%   Spacy, Brown clusters, WordNet
-%% - machine learner
-%% - tuning
-%% - feature templates
+\begin{figure*}
+\begin{dependency}[arc edge, text only label, theme=simple]
+  \begin{deptext}[column sep=.2cm]
+    i \& m \& fucking \& scared \& kill \& them \& d \& : \\
+   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
+  \end{deptext}
+  \depedge{2}{1}{\large nsubj}
+  \depedge{2}{8}{\large punct}
+  \depedge{2}{4}{\large acomp}
+  \depedge{4}{3}{\large amod}
+  \depedge{2}{5}{\large conj}
+  \depedge{5}{6}{\large dobj}
+  \depedge{5}{7}{\large advmod}
+  \deproot[edge unit distance=1.5ex]{2}{}
+\end{dependency}
+\caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
+\label{fig:dep}
+\end{figure*}
 
+\paragraph{Classifiers}
+
+\paragraph{Tuning}
+
+\paragraph{Features}
+Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
+\begin{description}
+\setlength\itemsep{0em}
+\item[Lexical] word form, lemma
+\item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
+\item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
+\end{description}
+These features are structured according to a set of \emph{feature
+  templates}, which introduce varying degrees of linear order and
+syntactic context: bag-of-features (unordered), bigrams, trigrams and
+dependency triples. These feature templates are applied to the feature
+types presented above, in order to yield features like the following
+for our examples sentence in Figure \ref{fig:dep}:
+
+\begin{itemize}
+\setlength\itemsep{0em}
+\item \{i m,  m fucking, fucking scared, scared kill, kill them,  them d,  d :\}
+
+\item \{PRON VERB VERB, VERB VERB ADJ, VERB ADJ VERB, ADJ VERB PRON,  VERB PRON X,  PRON X PUNCT\}
+
+\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
+\end{itemize}
+Our lexical features are very specific and require the exact
+combination of two lexical items in order to apply to a new instance.
+Following \newcite{Jos:Pen:2009}, we therefore experiment with
+generalization of features by backoff to a more general category,
+e.g. from word form to lemma or PoS. A dependency triple over word
+forms like $<$kill, dobj, them$>$ would thus be generalized to
+$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
+PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
+trigram and dependency triple features.
 \subsection{Results}
@@
 
-\subsection{Held-out results}
+\subsection{Held-out results}M
 

### 2016-02-17 submission.tex
Baseline results

@@
 corpus containing Reuters English newswire text, with approximately 63
-million words and 3.3 million sentences. We vary the number of clusters to be either 100,
-320, 1000 or 3200 clusters and use the full cluster label.
- WordNet REF
+million words and 3.3 million sentences. We vary the number of
+clusters to be either 100, 320, 1000 or 3200 clusters and use the full
+cluster label.  We also make use of the WordNet resource
+\cite{wordnet} to determine a word's synset, parent and grandparent
+synset.
 
 \begin{figure*}
+\begin{center}
 \begin{dependency}[arc edge, text only label, theme=simple]
@@
 \label{fig:dep}
+\end{center}
 \end{figure*}
@@
 \paragraph{Classifiers}
-
+Toolkits and references
 \paragraph{Tuning}
-
+Short on tuning
 \paragraph{Features}
@@
 trigram and dependency triple features.
-\subsection{Results}
+\subsection{Development results}
+Table \ref{tab:baseline} shows baseline results in terms of F-score
+for bag-of, bigram and trigram templates over lexical features (word
+form and lemma). The presented results constitute the best F-scores
+after tuning (which was only done on the MaxEnt classifier and the
+SVM, not on the random forest classifier), as discussed above. The
+overall best result came from the logistic regression classifier with
+the bag of word form feature set. Generally we see that feature sets
+containing bag of lexical features in some form outperform the
+$n$-gram feature sets.
+The feature set we will use as a baseline in the next stage of our
+experiments is bag of word forms. The feature set recieved an F-score
+of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$,
+using the MaxEnt classifier after tuning. We will also be
+using only the MaxEnt classifier for the remainder of the
+feature set experiments.
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{lrrr}
+      \toprule
+
+      & MaxEnt & SVM & Random Forest \\
+      \midrule
+      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $0.3582$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
+      Bag of lemmas & $0.5902$ & $0.5982$ & $0.3483$ \\
+      Bigrams & $0.4856$ & $0.4887$ & $\textbf{0.4683}$ \\
+      Trigrams & $0.2776$ & $0.2856$ & $0.2673$ \\
+
+      \bottomrule
+      % Data fra firstPass i classify
+      % Source/printFirstPassResults.py
+    \end{tabular}
+  \end{center}
+  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).}
+  \label{tab:baseline}
+\end{table*}
+
+Morphosyntactic features:
+- bag of, bigram, trigram of pos, deprel
+- combine with baseline
+
+Semantic features:
+- bag of, bigram, trigram of Brown, WordNet
+- combine with baseline
+
+Combination of best from baseline, morphosyntactic and semantic
 
@@
 
-\subsection{Held-out results}M
+\subsection{Held-out results}
 

### 2016-02-18 submission.tex
Minor changes
Updated Random forest results in baseline system table

@@
       \midrule
-      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $0.3582$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
-      Bag of lemmas & $0.5902$ & $0.5982$ & $0.3483$ \\
-      Bigrams & $0.4856$ & $0.4887$ & $\textbf{0.4683}$ \\
-      Trigrams & $0.2776$ & $0.2856$ & $0.2673$ \\
+      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
+      Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
+      Bigrams & $0.4856$ & $0.4887$ & $0.4944$ \\
+      Trigrams & $0.2776$ & $0.2856$ & $0.2859$ \\
 

### 2016-02-18 submission.tex
Added abstract

--- 2016-02-17 submission.tex
@@
 \begin{abstract}
-Here comes an abstract for this article
+This article investigates the effect of various types of linguistic
+features (lexical, morphosyntactic and semantic) for the task of
+detecting threats of violence in a data set of YouTube comments. It
+further examines the use of these features in combination with
+different representations of the linguistic context. Our results show that ...
 \end{abstract}
@@
 
+Backoff: best of morphosyntactic and semantic?
+
 Combination of best from baseline, morphosyntactic and semantic
+
+Held-out
 

### 2016-03-03 submission.tex
Added tuning and almost finished experiments

@@
 \usepackage{tikz-dependency}
+
+\usepackage{xytree} % Dependency tree
 
@@
 
+\begin{figure*}
+  \begin{center}
+
+    \xytext{
+      \xybarnode{i} &~~~&
+      \xybarnode{m}
+      \xybarconnect(UL,U){-2}"_{\small nsubj}"
+      \xybarconnect[21](UR,U){12}"^{\small punct}"
+      \xybarconnect[15](UR,UL){6}"^{\small conj}"
+      \xybarconnect[9](UR,U){4}"^{\small acomp}"
+      &~~~&
+      \xybarnode{fucking} &~~~&
+      \xybarnode{scared}
+      \xybarconnect(UL,U){-2}"_{\small amod}"
+      &~~~&
+      \xybarnode{kill}
+      \xybarconnect[9](U,U){4}"^{\small advmod}"
+      \xybarconnect(UR,U){2}"^{\small dobj}"
+      &~~~&
+      \xybarnode{them}
+      &~~~&
+      \xybarnode{d}
+      &~~~&
+      \xybarnode{:}
+    }
+    \caption{A visual representation of the dependency graph of our example sentence.}
+    \label{fig:dependencygraph}
+  \end{center}
+\end{figure*}
+
 \paragraph{Classifiers}
@@
 \paragraph{Tuning}
-Short on tuning
+When tuning each model, we aimed to maximize the F-score of the model.
+In the MaxEnt classifier and SVM we tuned the C-value, which for both classifiers is the inverse of regularization strength.
+When tuning these classifiers, we started with C-values from 1 to 150 in 10-value increments, selected the best performing C-value and repeated the process with ever decreasing increments, with the range of C-values centered on the best performing C-value thus far.
+After 6 iterations, we terminate the tuning, and select the best performing C-value.
+When tuning the RandomForest classifier, we performed a grid search over the max number features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
+
+When performing tuning on the MaxEnt classifier with the bag of words features set, F-score improved from $0.5622$, using the default settings (C-value = 1), to $0.6123$, using the best C-value ($11.25$).
+The large increase in F-score after tuning leads us to perform tuning on every feature set we test.
+
 \paragraph{Features}
@@
 form and lemma). The presented results constitute the best F-scores
-after tuning (which was only done on the MaxEnt classifier and the
-SVM, not on the random forest classifier), as discussed above. The
+after tuning, as discussed above. The
 overall best result came from the logistic regression classifier with
@@
 
-Morphosyntactic features:
-- bag of, bigram, trigram of pos, deprel
-- combine with baseline
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{lrrrrr}
+      \toprule
 
-Semantic features:
-- bag of, bigram, trigram of Brown, WordNet
-- combine with baseline
+      & Lemma & POS & Dep & Synset & Brown\\ % POS er uPOS
+      \midrule
+      Bag of Features & $0.5902$ & $0.0018$   &  $0.0143$ & $0.4922$ & $0.4688$ \\ % Synset regular, Brown 3200
+      BoW + Bag of Features & $0.6278$ & $0.6071$ & $0.6185$ & $0.6176$ & $0.6145$\\ % Synset regular, Brown100
 
-Backoff: best of morphosyntactic and semantic?
+      \bottomrule
 
-Combination of best from baseline, morphosyntactic and semantic
+    \end{tabular}
+  \end{center}
+  \caption{Results of bag of feature variations with different feature types. The results shown are the F-scores of each feature set after tuning, using the MaxEnt classifier.}
+  \label{tab:bagOfFeatures}
+\end{table*}
+
+Next, we add the different feature types.
+We first use the bag of features feature template, for each feature, both on its own, and in a feature set with bag of word forms.
+As seen in table \ref{tab:bagOfFeatures}, none of the feature types alone result in higher F-scores than bag of words.
+However, all feature types but the POS, combined with bag of words, perform better than bag of words alone, with the combination of bag of lemmas and bag of words performing best, with an F-score of $0.6278$.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lrrrr}
+      \toprule
+
+      & F-score \\
+      \midrule
+      Bag of words \& bigrams & $0.6376$ \\
+      Bag of words \& trigrams & $0.6180$ \\
+      Bag of words \& $n$-grams & $0.6337$ \\
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{F-scores of the bag of words feature sets, combined with word form bigrams, trigrams or both (termed simply $n$-grams in the table).}
+  \label{tab:ngrams}
+\end{table}
+
+Now we test word form $n$-grams with bag of words.
+As seen in table \ref{tab:ngrams}, we test bag of words combined with the word form variants of bigrams, trigrams and both.
+The best result comes from bag of words with only bigrams, with an F-score of $0.6376$, closely followed by bag of words with both types of $n$-grams, which got an F-score of $0.6337$.
+When we combine the $n$-grams combinations with both bag of words and bag of features, we get a new best result from bag of words, bag of lemmas and both types of $n$-grams, which gets an F-score of $0.6656$.
+
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{lrrrrrr}
+      \toprule
+      BoW, BoF \& & Lemma & POS & Dep & Synset & Brown\\
+      \midrule
+      Bigram + backoff & $0.6611$ & $0.6410$  & $0.6208$ & $0.6454$ & $0.6285$\\ % synset reg, b3200
+      Trigram + backoff & $0.6480$ & $0.6294$ & $0.6194$ & $0.6448$ & $0.6173$ \\ % synset reg, b320
+      $n$-gram + backoff & $0.6649$ & $0.6320$ & $0.6220$ & $0.6537$ & $0.6335$\\ % synset reg, b320
+      %Bigram + backoff, trigram & $\textbf{0.6649}$ & $0.6398$ & $0.6309$ & $0.6192$ \\
+      %Bigram, trigram + backoff & $\textbf{0.6649}$ & $0.6320$ & $\textbf{0.6368}$ & $\textbf{0.6220}$ \\
+      %Bigram + backoff, trigram + backoff & $0.6645$ & $0.6316$ & $0.6268$ & $0.6127$ \\
+
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{Bag of words, bag of features and different combinations of $n$-grams with feature backoff. Each backoff combination is the one that achieved the best result.}
+  \label{tab:ngrambackoff}
+\end{table*}
+
+Next we combine the results of bag of features, and $n$-grams, with $n$-gram feature backoffs.
+In table \ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the result of including backoff features.
+
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{lrrrrrr}
+      \toprule
+
+      & w/o backoff & Lemma & POS & Tag & Synset & Brown\\
+      \midrule
+      Dependency triples w/ backoff  BoW & $0.6240$ &  $0.6224$ & $0.6298$ & $0.6135$ & $0.6234$ & $0.6299$  \\ % Synset regular og grand parent, Brown 320
+      Dependency triples w/ backoff BoW, BoL \& n-grams & $0.6586$ & $0.6507$ & $0.6547$ & $0.6536$ & $0.6516$ & $0.6504$\\ % Synset gp, Brown 1000
+
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{F-scores of the different feature backoffs from dependency triples.}
+  \label{tab:firsttriplebackoff}
+\end{table*}
+
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{lrr}
+      \toprule
+
+      & BoW & Best\\
+      \midrule
+      w/o backoff & $0.6240$ & $0.6586$ \\
+      Lemma & $0.6224$ & $0.6507$ \\
+      POS & $0.6298$ & $0.6547$ \\ % uPOS, begge to
+      Dep \\
+      Synset & $0.6234$ & $0.6516$  \\ % 1. regular og granparent (de er like), 2. grand parent
+      Brown & $0.6299$ & $0.6504$ \\ % 1. Brown 320, 2. Brown 1000
+
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{BoW is BoW \& dep triples, Best is BoW, BoL, n-grams \& dep triples}
+  \label{tab:firsttriplebackoff}
+\end{table*}
+
+Add dependency triples, add dependency backoff, no improvement. Construct final model, no improvement.
+
+%% Morphosyntactic features:
+%% - bag of, bigram, trigram of pos, deprel
+%% - combine with baseline
+
+%% Semantic features:
+%% - bag of, bigram, trigram of Brown, WordNet
+%% - combine with baseline
+
+%% Backoff: best of morphosyntactic and semantic?
+
+%% Combination of best from baseline, morphosyntactic and semantic
 

### 2016-03-03 submission.tex
Changed some of the tables

@@
 
-\begin{figure*}
+\begin{figure}
 \begin{verbatim}
 timpa666
-1    and i will kill every fucking muslim and arab!
+1    and i will kill every
+     fucking muslim and arab!
 
@@
 0    Need a solution?
-1    Drop one good ol' nuke on that black toilet in Mecca.
+1    Drop one good ol' nuke on
+     that black toilet in Mecca.
 
 Ammar Alozaibi
-1    Funny, We will conquer you all in just few years, U will be
-     my slave and your women will be my Sex Toy in Bed.
+1    Funny, We will conquer you
+     all in just few years, U will
+     be my slave and your women
+     will be my Sex Toy in Bed.
 
@@
 \label{fig:comments}
-\end{figure*}
+\end{figure}
 
@@
 feature set experiments.
-\begin{table*}
+\begin{table}
   \begin{center}
@@
 
-      & MaxEnt & SVM & Random Forest \\
+      & MaxEnt & SVM & RF \\
       \midrule
@@
   \end{center}
-  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).}
+  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).
+MaxEnt is the MaximumEntropy classifier, SVM is the support vector machine, and RF is the RandomForest classifier.}
   \label{tab:baseline}
-\end{table*}
+\end{table}
 
@@
 
-\begin{table*}
+\begin{table}
   \begin{center}
@@
   \label{tab:firsttriplebackoff}
-\end{table*}
+\end{table}
 

### 2016-03-03 submission.tex
Changed some formatting

@@
 \usepackage{xytree} % Dependency tree
+\usepackage{fancyvrb} % Comments verbatim
 
@@
 either a \tov{} (or support for a \tov{}) or not. The data set
-furthermore records the username\footnote{In 2013, YouTube changed its
-  commenting system from using unique usernames, to using "real
-  names", like Facebook and other sites \cite{youtube2013}. Some
-  accounts, however, did not provide real names, so they continue to
-  only be identified by their usernames.} of the user that posted the
+furthermore records the username\footnote{The usernames were annonymized by us}
+%% \footnote{In 2013, YouTube changed its
+%%   commenting system from using unique usernames, to using "real
+%%   names", like Facebook and other sites \cite{youtube2013}. Some
+%%   accounts, however, did not provide real names, so they continue to
+%%   only be identified by their usernames.}
+  of the user that posted the
 comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
@@
 \begin{figure}
-\begin{verbatim}
-timpa666
+\begin{Verbatim}[fontsize=\small]
+User #44
 1    and i will kill every
@@
 
-NimsXdimensions
+User #88
 0    Need a solution?
@@
 
-Ammar Alozaibi
+User #138
 1    Funny, We will conquer you
@@
      will be my Sex Toy in Bed.
-
-\end{verbatim}
+\end{Verbatim}
 \caption{Examples of comments from the data set.}

### 2016-03-03 submission.tex
Shortened previous work section

@@
 
-\newcite{dinakar2011} proposes a method for the detection of
+\newcite{dinakar2011} propose a method for the detection of
 cyberbullying by targeting combinations of profane or negative words,
@@
 data set consists of over 50,000 YouTube comments taken from videos
-about controversial topics. They adopt a two-stage approach, where the
-first stage consists of using a lexicon of negative words and a list
-of profane words, as well as part-of-speech tags from the training
-data that were correlated with bullying. The second stage is
-category-specific, and makes use of commonly observed uni- and bigrams
-from each category as features. The experiments reported accuracies
-from 63~\% to 80~\%, but did not report precision or recall.
+about controversial topics. %% They adopt a two-stage approach, where the
+%% first stage consists of using a lexicon of negative words and a list
+%% of profane words, as well as part-of-speech tags from the training
+%% data that were correlated with bullying. The second stage is
+%% category-specific, and makes use of commonly observed uni- and bigrams
+%% from each category as features.
+The experiments reported accuracies from 63~\% to 80~\%, but did not
+report precision or recall.
 % lists of negative and profane words
@@
 There has been quite a bit of work focused on the detection of threats
-in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
-The data set used for these experiments consists of a collection of 5000
-threatening tweets collected by a website over a period of about two
-years. In addition, a large number of random tweets were collected for
-development and testing. A set of 2.3 million random tweets was used
-for development, and a set of 1 million was used for testing. 
+in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000
+threatening tweets collected by a website. In addition, a large number of random tweets were collected for
+development and testing. %% A set of 2.3 million random tweets was used
+%% for development, and a set of 1 million was used for testing.
 The system relies on manually constructed recognition patterns, in the
-form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
-trigrams), but do not go into detail about the methods used to
-construct these patterns, stating that the researchers relied on their
-(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
+form of n-grams 
+%(uni-, bi- and trigrams, as well as skip bi- and trigrams)
+, but do not go into detail about the methods used to
+construct these patterns%% , stating that the researchers relied on their
+%% (linguistic) intuition as speakers of Dutch \cite{nellngram2013}
+. In
 \newcite{nellshallow2013}, a manually crafted shallow parser is added
 to the system. This improves results to a precision of 39\% and a
-recall of 59\% \footnote{Perhaps a footnote on the peculiarities of the evaluation??}.
+recall of 59\%.
 % handcrafted patterns
@@
 
-\newcite{warner2012} present a method for detecting unwanted or
-illegal comments in user-generated web text from the internet, which
-relies on machine learning in combination with template-based
-features. The data set used in the research came from two sources. The
-first consists of posts from Yahoo news groups, the second were
-webpages collected by the American Jewish Congress that had been
-identified as offensive. The data set was manually annotated, and then
-the hate speech was assigned to a category, such as anti-Semitic,
-anti-woman, anti-Asian, etc. The task is then approached as a
-word-sense disambiguation task, since the same words can be used in
-both hateful and non-hateful contexts. The features used in the
-classification were combinations of uni-, bi- and trigrams,
-part-of-speech-tags and Brown clusters.  The best results of the
-classifications were obtained using only unigrams as features, with a
-precision of 67~\% and a recall of 60~\%. The other feature sets
-garnered much lower results, and the authors suggest that deeper
+\newcite{warner2012} present a method for detecting hate speech in
+user-generated web text from the internet, which relies on machine
+learning in combination with template-based features. The task
+is approached as a word-sense disambiguation task, since the same
+words can be used in both hateful and non-hateful contexts. The
+features used in the classification were combinations of uni-, bi- and
+trigrams, part-of-speech-tags and Brown clusters.  The best results of
+the classifications were obtained using only unigrams as features,
+with a precision of 67~\% and a recall of 60~\%. The other feature
+sets garnered much lower results, and the authors suggest that deeper
 parsing could reveal significant phrase patterns.
@@
 
-\newcite{hammer2014} reports an experiment on the data set that we
-will be using in our own experiments, although it has been changed
-slightly since the publication of his initial study. The method used a
-logistic LASSO regression analysis on bigrams (skip-grams) of
-important words to classify sentences as \tovs{} or not.
-The method described in the article uses a set of important words that
-are correlated with threats of violence. The features are bigrams of
-two of these important words observed in the same sentence. The
-article does not describe exactly how these important words were
-selected, stating only that words were chosen that were significantly
-correlated with the response (violent/non-violent sentence).
-Results are reported only in terms of proportion of false positives for the two classes and it is not clear how the data was split for training and evaluation.
+Perhaps closest to the current work is the work of
+\newcite{hammer2014}, who reports on an experiment on the same data set that
+we will be using in our own experiments. The method uses a logistic
+LASSO regression analysis on bigrams (skip-grams) of important words
+to classify sentences as \tovs{} or not.  The system makes use of a
+list of words that are correlated with threats of violence. The
+article does not, however, describe exactly how these important words
+were selected, stating only that words were chosen that were
+significantly correlated with the response (violent/non-violent
+sentence). Results are reported only in terms of proportion of false
+positives for the two classes and it is not clear how the data was
+split for training and evaluation, which makes it difficult to compare with their results.
 

### 2016-03-03 submission.tex
Modified depgraph
Added all but the conclusion sections

--- 2016-03-03 submission.tex
@@
 \usepackage{fancyvrb} % Comments verbatim
+\usepackage{fixltx2e} % For subscript i tekst (F_1 measure)
+\usepackage{enumitem} % Kompakt liste
 
@@
 % if the names do not fit well on one line use
+
 %         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
@@
 
-  & Commments  & Sentences  & Users posting \\
+  & Comments  & Sentences  & Users posting \\
   \midrule
@@
 Figure \ref{fig:comments} provides some examples of comments containing
-\tovs{} taken from the data set. The first line is the username or
-name, and the subsequent lines are the sentences of the comment. An
+\tovs{} taken from the data set. The first line is the annonymized username, and the subsequent lines are the sentences of the comment. An
 empty line indicates the end of a comment. The sentences are annotated
@@
 User #44
-1    and i will kill every
-     fucking muslim and arab!
+1    and i will kill every fucking
+     muslim and arab!
 
@@
 0    Need a solution?
-1    Drop one good ol' nuke on
-     that black toilet in Mecca.
-
-User #138
-1    Funny, We will conquer you
-     all in just few years, U will
-     be my slave and your women
-     will be my Sex Toy in Bed.
+1    Drop one good ol' nuke on that
+     black toilet in Mecca.
 \end{Verbatim}
@@
 
-\begin{figure*}
-  \begin{center}
+%% \begin{figure*}
+%%   \begin{center}
 
-    \xytext{
-      \xybarnode{i} &~~~&
-      \xybarnode{m}
-      \xybarconnect(UL,U){-2}"_{\small nsubj}"
-      \xybarconnect[21](UR,U){12}"^{\small punct}"
-      \xybarconnect[15](UR,UL){6}"^{\small conj}"
-      \xybarconnect[9](UR,U){4}"^{\small acomp}"
-      &~~~&
-      \xybarnode{fucking} &~~~&
-      \xybarnode{scared}
-      \xybarconnect(UL,U){-2}"_{\small amod}"
-      &~~~&
-      \xybarnode{kill}
-      \xybarconnect[9](U,U){4}"^{\small advmod}"
-      \xybarconnect(UR,U){2}"^{\small dobj}"
-      &~~~&
-      \xybarnode{them}
-      &~~~&
-      \xybarnode{d}
-      &~~~&
-      \xybarnode{:}
-    }
-    \caption{A visual representation of the dependency graph of our example sentence.}
-    \label{fig:dependencygraph}
-  \end{center}
-\end{figure*}
+%%     \xytext{
+%%       \xybarnode{i} &~~~&
+%%       \xybarnode{m}
+%%       \xybarconnect(UL,U){-2}"_{\small nsubj}"
+%%       \xybarconnect[21](UR,U){12}"^{\small punct}"
+%%       \xybarconnect[15](UR,UL){6}"^{\small conj}"
+%%       \xybarconnect[9](UR,U){4}"^{\small acomp}"
+%%       &~~~&
+%%       \xybarnode{fucking} &~~~&
+%%       \xybarnode{scared}
+%%       \xybarconnect(UL,U){-2}"_{\small amod}"
+%%       &~~~&
+%%       \xybarnode{kill}
+%%       \xybarconnect[9](U,U){4}"^{\small advmod}"
+%%       \xybarconnect(UR,U){2}"^{\small dobj}"
+%%       &~~~&
+%%       \xybarnode{them}
+%%       &~~~&
+%%       \xybarnode{d}
+%%       &~~~&
+%%       \xybarnode{:}
+%%     }
+%%     \caption{A visual representation of the dependency graph of our example sentence.}
+%%     \label{fig:dependencygraph}
+%%   \end{center}
+%% \end{figure*}
 
 \paragraph{Classifiers}
-Toolkits and references
+
+We will test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a RandomForest classifier (RF).
+\newcite{scikit-learn} describes scikit-learn, the Python module we use for our classification.
+
 \paragraph{Tuning}
@@
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
-When tuning the RandomForest classifier, we performed a grid search over the max number features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
+When tuning the RandomForest classifier, we performed a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
 
-When performing tuning on the MaxEnt classifier with the bag of words features set, F-score improved from $0.5622$, using the default settings (C-value = 1), to $0.6123$, using the best C-value ($11.25$).
+When performing tuning on the MaxEnt classifier with the bag of words features set, F-score improved from $0.5622$, using the default settings (C-value=1), to $0.6123$, using the best C-value ($11.25$).
 The large increase in F-score after tuning leads us to perform tuning on every feature set we test.
@@
 Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
-\begin{description}
-\setlength\itemsep{0em}
-\item[Lexical] word form, lemma
-\item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
-\item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
-\end{description}
+
+\begin{itemize}[noitemsep]
+\item Lexical:
+  \begin{itemize}[noitemsep]
+  \item Word form
+  \item Lemma
+  \end{itemize}
+
+\item Morphosyntactic:
+  \begin{itemize}[noitemsep]
+  \item Penn Treebank (PTB) POS
+  \item Universal (uPOS) PoS
+  \item Dependency Relation
+  \end{itemize}
+
+\item Semantic:
+  \begin{itemize}[noitemsep]
+    \item Brown cluster label (100, 320, 1000 and 3200 clusters)
+    \item WordNet synset, parent synset and grandparent synset
+  \end{itemize}
+\end{itemize}
+
+%% \begin{description}
+%% \setlength\itemsep{0em}
+%% \item[Lexical] word form, lemma
+%% \item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
+%% \item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
+%% \end{description}
 These features are structured according to a set of \emph{feature
@@
 trigram and dependency triple features.
+
 \subsection{Development results}
-Table \ref{tab:baseline} shows baseline results in terms of F-score
-for bag-of, bigram and trigram templates over lexical features (word
-form and lemma). The presented results constitute the best F-scores
-after tuning, as discussed above. The
-overall best result came from the logistic regression classifier with
-the bag of word form feature set. Generally we see that feature sets
-containing bag of lexical features in some form outperform the
-$n$-gram feature sets.
-The feature set we will use as a baseline in the next stage of our
-experiments is bag of word forms. The feature set recieved an F-score
-of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$,
-using the MaxEnt classifier after tuning. We will also be
-using only the MaxEnt classifier for the remainder of the
-feature set experiments.
+
+During development, we first select a baseline system, consisting of a feature set of lexical features (word forms and lemmas) and a classifier, that we will compare the other results to.
+Next, we will test different combinations of the lexical feature sets from the baseline.
+We will then introduce more linguistic features, both morphosyntactic and semantic, as bags of features, and as backoff from word form $n$-grams.
+Lastly we will evaluate the inclusion of dependency triples, using both word form triples, and dependency triples with feature backoff.
+
 \begin{table}
@@
 
-\begin{table*}
+Table \ref{tab:baseline} shows baseline results in terms of F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma) for the three different classifiers.
+The presented results constitute the best F-scores after tuning, as discussed above.
+The overall best result came from the MaxEnt classifier with the bag of word form feature set.
+Generally, we see that feature sets containing bag of lexical features in some form outperform the $n$-gram feature sets.
+The feature set we will use as a baseline in the next stage of our experiments is bag of word forms.
+The feature set recieved an F-score of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$, using the MaxEnt classifier after tuning.
+We will also be using only the MaxEnt classifier for the remainder of the feature set experiments.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lrrr}
+      \toprule
+
+      $n$-gram combination & BoW & BoW \& BoL \\
+      \midrule
+      no $n$-grams & $0.6123$ & $0.6278$ \\
+      bigrams & $\textbf{0.6376}$ & $0.6577$ \\
+      trigrams & $0.6180$ & $0.6453$ \\
+      $n$-grams & $0.6337$ & $\textbf{0.6656}$ \\
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{F-scores of the bag of words feature sets, combined with word form bigrams, trigrams or both (termed simply $n$-grams in the table).}
+  \label{tab:ngrams}
+  % tidligere Tabell 4
+\end{table}
+
+\begin{table}
   \begin{center}
@@
 
-      & Lemma & POS & Dep & Synset & Brown\\ % POS er uPOS
+     & POS\textsubscript{Lex} & Dep\textsubscript{Lex} & Synset & Brown\\ % POS er uPOS
       \midrule
-      Bag of Features & $0.5902$ & $0.0018$   &  $0.0143$ & $0.4922$ & $0.4688$ \\ % Synset regular, Brown 3200
-      BoW + Bag of Features & $0.6278$ & $0.6071$ & $0.6185$ & $0.6176$ & $0.6145$\\ % Synset regular, Brown100
+      BoF & $0.6018$ & $0.5655$ & $0.4922$ & $0.4688$ \\ % Synset regular, Brown 3200
+      %% BoF & $0.0018$  &  $0.0143$ & $0.4922$ & $0.4688$ \\ % Synset regular, Brown 3200
+      BoW+BoF & $0.6071$ & $0.6185$ & $0.6176$ & $0.6145$\\ % Synset regular, Brown100
 
@@
   \label{tab:bagOfFeatures}
-\end{table*}
+  % tidligere Tabell 3
+\end{table}
+
+Now we test word form $n$-grams with bag of lexical features.
+As seen in table \ref{tab:ngrams}, we test bag of words alone, and bag of words with bag of lemmas, combined with the word form variants of bigrams, trigrams and both.
+The best result without bag of lemmas comes from bag of words with only bigrams, with an F-score of $0.6376$, closely followed by bag of words with both types of $n$-grams, which got an F-score of $0.6337$.
+The best overall result, by far, came from the combination of bag of words, bag of lemmas, and both types of $n$-grams, which got an F-score of $0.6656$.
 
@@
   \begin{center}
-    \begin{tabular}{lrrrr}
-      \toprule
-
-      & F-score \\
-      \midrule
-      Bag of words \& bigrams & $0.6376$ \\
-      Bag of words \& trigrams & $0.6180$ \\
-      Bag of words \& $n$-grams & $0.6337$ \\
-      \bottomrule
-
-    \end{tabular}
-  \end{center}
-  \caption{F-scores of the bag of words feature sets, combined with word form bigrams, trigrams or both (termed simply $n$-grams in the table).}
-  \label{tab:ngrams}
-\end{table}
-
-Now we test word form $n$-grams with bag of words.
-As seen in table \ref{tab:ngrams}, we test bag of words combined with the word form variants of bigrams, trigrams and both.
-The best result comes from bag of words with only bigrams, with an F-score of $0.6376$, closely followed by bag of words with both types of $n$-grams, which got an F-score of $0.6337$.
-When we combine the $n$-grams combinations with both bag of words and bag of features, we get a new best result from bag of words, bag of lemmas and both types of $n$-grams, which gets an F-score of $0.6656$.
-
-\begin{table*}
-  \begin{center}
     \begin{tabular}{lrrrrrr}
       \toprule
-      BoW, BoF \& & Lemma & POS & Dep & Synset & Brown\\
+      %% BoW, BoF \& 
+      %% & Lemma & POS & Dep & Synset & Brown\\
+      %% \midrule
+      %% Bigram + backoff
+      %%  \\ % synset reg, b3200
+      %% Trigram + backoff
+      %%  \\ % synset reg, b320
+      %% $n$-gram + backoff 
+      %% \\ % synset reg, b320
+
+      & bigram+ & trigram+ & $n$-gram+ \\
       \midrule
-      Bigram + backoff & $0.6611$ & $0.6410$  & $0.6208$ & $0.6454$ & $0.6285$\\ % synset reg, b3200
-      Trigram + backoff & $0.6480$ & $0.6294$ & $0.6194$ & $0.6448$ & $0.6173$ \\ % synset reg, b320
-      $n$-gram + backoff & $0.6649$ & $0.6320$ & $0.6220$ & $0.6537$ & $0.6335$\\ % synset reg, b320
+      Lemma & $0.6611$ & $0.6480$ &  $\textbf{0.6649}$ \\ 
+      POS & $\textbf{0.6410}$ & $0.6294$ & $0.6320$ \\
+      Dep & $0.6208$ & $0.6194$ & $\textbf{0.6220}$ \\
+      Synset & $0.6454$ & $0.6448$ &  $\textbf{0.6537}$\\
+      Brown & $0.6285$ &  $0.6173$  & $\textbf{0.6335}$\\
+
       %Bigram + backoff, trigram & $\textbf{0.6649}$ & $0.6398$ & $0.6309$ & $0.6192$ \\
@@
   \label{tab:ngrambackoff}
-\end{table*}
+\end{table}
 
@@
 In table \ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the result of including backoff features.
-
-\begin{table*}
-  \begin{center}
-    \begin{tabular}{lrrrrrr}
-      \toprule
-
-      & w/o backoff & Lemma & POS & Tag & Synset & Brown\\
-      \midrule
-      Dependency triples w/ backoff  BoW & $0.6240$ &  $0.6224$ & $0.6298$ & $0.6135$ & $0.6234$ & $0.6299$  \\ % Synset regular og grand parent, Brown 320
-      Dependency triples w/ backoff BoW, BoL \& n-grams & $0.6586$ & $0.6507$ & $0.6547$ & $0.6536$ & $0.6516$ & $0.6504$\\ % Synset gp, Brown 1000
-
-      \bottomrule
-
-    \end{tabular}
-  \end{center}
-  \caption{F-scores of the different feature backoffs from dependency triples.}
-  \label{tab:firsttriplebackoff}
-\end{table*}
 
@@
 
-      & BoW & Best\\
+      Dependency backoff & Simple & Combined\\
       \midrule
-      w/o backoff & $0.6240$ & $0.6586$ \\
+      w/o backoff & $0.6240$ & $\textbf{0.6586}$ \\
       Lemma & $0.6224$ & $0.6507$ \\
-      POS & $0.6298$ & $0.6547$ \\ % uPOS, begge to
-      Dep \\
+      POS & $\textbf{0.6298}$ & $0.6547$ \\ % uPOS, begge to
       Synset & $0.6234$ & $0.6516$  \\ % 1. regular og granparent (de er like), 2. grand parent
@@
   \end{center}
-  \caption{BoW is BoW \& dep triples, Best is BoW, BoL, n-grams \& dep triples}
-  \label{tab:firsttriplebackoff}
+  \caption{Simple is the feature set containing Bag of Words and dependency triples.
+Combined is the feature set containing Bag of Words, bag of Lemmas, bigrams, trigrams and dependency triples.
+Each row backs off to a different feature type.}
+  \label{tab:depbackoff}
 \end{table}
 
-Add dependency triples, add dependency backoff, no improvement. Construct final model, no improvement.
+Lastly, we will test the addition of dependency triples to our models.
+We add dependency triples consisting of word forms, both alone, and in conjunction with feature backoffs.
+As with $n$-gram backoff, we test multiple variations of backoff, both head-backoff and modifier-backoff.
+The results reported are the backoff variant that acheived the best results.
+As seen in  table \ref{tab:depbackoff}, the inclusion of word form dependency triples improved upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for bag of words alone.
+Dependency triples did not, however, improve upon the results achieved by our best model, as the model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
+
+The addition of backoff also did not improve upon our best model.
+Adding POS backoff to our simplest model resulted in a slightly increased F-score of $0.6298$.
+Adding backoff to our combined model, however, only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.
+
+Our final model is the model consisting of bag of word forms, bag of lemmas, and word form bigrams and trigrams, which got the best result, with an F-score of $0.6656$.
+In subsection \ref{sec:heldout} we will also test that same model with the addition of bigram backoff to lemmas, which got an F-score of $0.6649$.
 
@@
 
-Held-out
-
 \subsection{Error analysis}
 
+Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set.
+Our best model is the feature sets containing bag of words, bag of lemmas, and word form bigrams and trigrams.
+As seen in table \ref{tab:positives}, our classification of the development set using the best model resulted in $646$ true positives, $192$ false positives, and $457$ false negatives.
+This results in a precision of $0.7709$, and a recall of $0.5857$.
+Compared with our baseline system, which had a precision of $0.6777$, and a recall of $0.5585$, we see that the majority of the improvement over the baseline comes from the increase in precision.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{llrr}
+      \toprule
+
+      & & Actual & \\
+      &  & Positive & Negative\\
+      \midrule
+      Predicted & Positive & $646$ & $192$ \\
+      & Negative & $457$ & $21,663$ \\
+
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{The true and false, positives and negatives of our best model, when classifying the development set.
+The numbers are the sum of each of the 10 classification, when performing 10-fold cross-validation.}
+  \label{tab:positives}
+\end{table}
+
+When reviewing a random subsample of the false positives and false negatives, we see that the noisy data has caused some problems for the preprocessor.
+Another source of errors, specifically false positives, are comments which use multiple typically threatening words in a non-threatening context.
+
 \subsection{Held-out results}
+\label{sec:heldout}
+
+We performed our final testing on the held-out test set using the baseline feature set, the combined feature set, and the combined features set with trigram backoff using lemma features.
+As seen in table \ref{tab:heldout}, the both the best feature set, and the second best, from our development testing outperformed the baseline feature set.
+The best feature set from development also outperformed the second best.
+The difference in F-score was not as large as in our development testing, however.
+This may be due to the fact that the baseline performed a lot better in the held-out testing compared to the development testing, with an F-score of $0.6562$.
+The F-scores of the combined feature sets were $0.6860$ and $0.6799$.
+In fact, both the combined feature sets improved upon the baseline in both precision, recall and F-scores.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lrrr}
+      \toprule
+
+      & Precision & Recall & F-score\\
+      \midrule
+      Baseline & $0.7325$ & $0.5943$ & $0.6562$ \\
+      Combined & $0.7532$ & $0.6299$ & $0.6860$  \\
+      Combined+ & $0.7703$ & $0.6085$ & $0.6799$ \\
+
+      \bottomrule
+
+    \end{tabular}
+  \end{center}
+  \caption{Precision, recall and F-score for the baseline feature set, the best feature set, and the best backoff feature set, when classification is performed on the held-out test set.}
+  \label{tab:heldout}
+\end{table}
 

### 2016-03-04 submission.tex

@@
 \begin{center}
-\begin{dependency}[arc edge, text only label, theme=simple]
+\begin{dependency}
+%\begin{dependency}[arc edge, text only label, theme=simple]
   \begin{deptext}[column sep=.2cm]
@@
   \depedge{2}{1}{\large nsubj}
-  \depedge{2}{8}{\large punct}
+  \depedge[edge unit distance=2ex]{2}{8}{\large punct}
   \depedge{2}{4}{\large acomp}
@@
   \depedge{5}{7}{\large advmod}
-  \deproot[edge unit distance=1.5ex]{2}{}
+ \deproot{2}{root}
 \end{dependency}

### 2016-03-04 submission.tex
Added to abstract

@@
 %todo: possibly a title that reflects the work better? 
+% Features for threat detection of user-generated text?
 \title{Detecting threats of violence in YouTube comments}
@@
 further examines the use of these features in combination with
-different representations of the linguistic context. Our results show that ...
+different representations of linguistic context and feature backoff. Our results show that combinations of lexical features outperform the use of more complex linguistic features for this task.
 \end{abstract}

### 2016-03-04 submission.tex
Added to abstract
Added new title

@@
 %todo: possibly a title that reflects the work better?
-% Features for threat detection of user-generated text?
-\title{Detecting threats of violence in YouTube comments}
+
+\title{Features for detecting threats of violence in YouTube comments}
+%\title{Detecting threats of violence in YouTube comments}
 
@@
 further examines the use of these features in combination with
-different representations of linguistic context and feature backoff. Our results show that combinations of lexical features outperform the use of more complex linguistic features for this task.
+different representations of linguistic context and feature backoff.
+Our results show that combinations of lexical features outperform the use of more complex syntactic and semantic features for this task.
 \end{abstract}

### 2016-03-06 submission.tex
Finished article for first delivery

@@
 This article investigates the effect of various types of linguistic
-features (lexical, morphosyntactic and semantic) for the task of
+features (lexical, morphosyntactic and lexical semantic) for the task of
 detecting threats of violence in a data set of YouTube comments. It
 further examines the use of these features in combination with
-different representations of linguistic context and feature backoff.
+different representations of linguistic context, and feature backoff.
 Our results show that combinations of lexical features outperform the use of more complex syntactic and semantic features for this task.
@@
 %% from each category as features.
-The experiments reported accuracies from 63~\% to 80~\%, but did not
+The experiments reported accuracies from 0.63 to 0.80, but did not
 report precision or recall.
@@
 \newcite{nellshallow2013}, a manually crafted shallow parser is added
-to the system. This improves results to a precision of 39\% and a
-recall of 59\%.
+to the system. This improves results to a precision of 0.39 and a
+recall of 0.59.
 % handcrafted patterns
@@
 the classifications were obtained using only unigrams as features,
-with a precision of 67~\% and a recall of 60~\%. The other feature
+with a precision of 0.67 and a recall of 0.60. The other feature
 sets garnered much lower results, and the authors suggest that deeper
@@
 Perhaps closest to the current work is the work of
-\newcite{hammer2014}, who reports on an experiment on the same data set that
+\newcite{hammer2014}, which reports on an experiment on the same data set that
 we will be using in our own experiments. The method uses a logistic
 LASSO regression analysis on bigrams (skip-grams) of important words
-to classify sentences as \tovs{} or not.  The system makes use of a
+to classify sentences as either \tovs{} or not.  The system makes use of a
 list of words that are correlated with threats of violence. The
@@
 sentence). Results are reported only in terms of proportion of false
-positives for the two classes and it is not clear how the data was
-split for training and evaluation, which makes it difficult to compare with their results.
+positives for the two classes, and it is not clear how the data was
+split for training and evaluation. This makes it difficult to compare our results to those of \newcite{hammer2014}.
 
@@
 consists of a set of sentences, each of them manually annotated to be
-either a \tov{} (or support for a \tov{}) or not. The data set
-furthermore records the username\footnote{The usernames were annonymized by us}
+either a \tov{} (or support for a \tov{}), or not. The data set
+furthermore records the username
 %% \footnote{In 2013, YouTube changed its
@@
 The data set consists of 9,845 comments, comprised of 28,643
-sentences, see table \ref{tab:dataset}. In total there are 402,673
-tokens in the sentences in the data set. There are 1,285 comments
+sentences, see Table \ref{tab:dataset}.
+%% In total there are 402,673 tokens in the sentences in the data set.
+There are 1,285 comments
 containing threats, and 1,384 sentences containing threats, as seen in
-table \ref{tab:dataset}.  \newcite{hammer2014} report inter annotator
+Table \ref{tab:dataset}.  \newcite{hammer2014} reports inter-annotator
 agreement on this data set to be 98~\%, as calculated on 120 of the
@@
 \end{center}
-\caption{Number of comments, sentences and users in \ds{}}
+\caption{Number of comments, sentences and users in \ds{}.}
 \label{tab:dataset}
@@
 Figure \ref{fig:comments} provides some examples of comments containing
-\tovs{} taken from the data set. The first line is the annonymized username, and the subsequent lines are the sentences of the comment. An
-empty line indicates the end of a comment. The sentences are annotated
+\tovs{} taken from the data set. The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
+%% An empty line indicates the end of a comment.
+The sentences are annotated
 with a number indicating whether they contain a \tov{} (1), or not
@@
 \label{sec:exp}
-Much of the previous work in Section \ref{sec:prev} made use of
+Much of the previous work presented in Section \ref{sec:prev} made use of
 precompiled lists of correlated words and manually crafted
@@
 previous work further highlights the effectiveness of lexical features
-(words-based features), however, several of the authors suggest that parsing
+(word-based features), however, several of the authors suggest that parsing
 may be beneficial for these tasks.
 
-In this work we experiment with a wide range of linguistic information
-as features in our system and investigate the introduction of
+In this work we experiment with a wide range of linguistic features in our system and investigate the introduction of
 linguistic context through a set of feature templates. We also
 generalize these features through a backoff technique. Throughout, we
-make use of freely available, re-usable resources and tools in order
+make use of resources and tools that are freely available and reusable in order
 to construct our system.
@@
 algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
-corpus containing Reuters English newswire text, with approximately 63
-million words and 3.3 million sentences. We vary the number of
+corpus containing Reuters English newswire text.
+%, with approximately 63 million words and 3.3 million sentences.
+We vary the number of
 clusters to be either 100, 320, 1000 or 3200 clusters and use the full
@@
 
-\begin{figure*}
+%% \begin{figure*}
+%% \begin{center}
+%% \begin{dependency}
+%% %\begin{dependency}[arc edge, text only label, theme=simple]
+%%   \begin{deptext}[column sep=.2cm]
+%%     i \& m \& fucking \& scared \& kill \& them \& d \& : \\
+%%    \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
+%%   \end{deptext}
+%%   \depedge{2}{1}{\large nsubj}
+%%   \depedge[edge unit distance=2ex]{2}{8}{\large punct}
+%%   \depedge{2}{4}{\large acomp}
+%%   \depedge{4}{3}{\large amod}
+%%   \depedge{2}{5}{\large conj}
+%%   \depedge{5}{6}{\large dobj}
+%%   \depedge{5}{7}{\large advmod}
+%%  \deproot{2}{root}
+%% \end{dependency}
+%% \caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
+%% \label{fig:dep}
+%% \end{center}
+%% \end{figure*}
+
+\begin{figure}
 \begin{center}
@@
   \begin{deptext}[column sep=.2cm]
-    i \& m \& fucking \& scared \& kill \& them \& d \& : \\
-   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
+    i \& m \& fucking \& scared \& kill \& them \& d\\
+   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \\
   \end{deptext}
   \depedge{2}{1}{\large nsubj}
-  \depedge[edge unit distance=2ex]{2}{8}{\large punct}
+  %% \depedge[edge unit distance=2ex]{2}{8}{\large punct}
   \depedge{2}{4}{\large acomp}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 
-We will test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a RandomForest classifier (RF).
-\newcite{scikit-learn} describes scikit-learn, the Python module we use for our classification.
+We test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a RandomForest classifier (RF).
+We approach the task as a binary classification task, and we use scikit-learn \cite{scikit-learn} for our classification.
 
 \paragraph{Tuning}
-When tuning each model, we aimed to maximize the F-score of the model.
-In the MaxEnt classifier and SVM we tuned the C-value, which for both classifiers is the inverse of regularization strength.
-When tuning these classifiers, we started with C-values from 1 to 150 in 10-value increments, selected the best performing C-value and repeated the process with ever decreasing increments, with the range of C-values centered on the best performing C-value thus far.
+When tuning each model, we aim to maximize the F-score of the model.
+In the MaxEnt classifier and SVM we tune the C-value, which for both classifiers is the inverse of regularization strength.
+When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with ever-decreasing increments, with the range of C-values centered on the best performing C-value thus far.
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
-When tuning the RandomForest classifier, we performed a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
+When tuning the RandomForest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
+In the following experiments, we perform tuning on all feature sets.
 
-When performing tuning on the MaxEnt classifier with the bag of words features set, F-score improved from $0.5622$, using the default settings (C-value=1), to $0.6123$, using the best C-value ($11.25$).
+% TODO: Ta med siste setning, om at vi alltid tuner
+%% When performing tuning on the MaxEnt classifier with the bag of words features set, F-score improved from $0.5622$, using the default settings (C-value=1), to $0.6123$, using the best C-value ($11.25$).
 The large increase in F-score after tuning leads us to perform tuning on every feature set we test.
@@
 \paragraph{Features}
-Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
+Based on the enriched data set, as described above, we experiment with the following feature types:
 
@@
 \setlength\itemsep{0em}
-\item \{i m,  m fucking, fucking scared, scared kill, kill them,  them d,  d :\}
+\item Bigrams of word forms: \{i m,  m fucking, fucking scared, ...\}
 
-\item \{PRON VERB VERB, VERB VERB ADJ, VERB ADJ VERB, ADJ VERB PRON,  VERB PRON X,  PRON X PUNCT\}
-
-\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
+\item Depdendency triples: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, ... \}
 \end{itemize}
@@
 forms like $<$kill, dobj, them$>$ would thus be generalized to
-$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
+$<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj,
 PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
@@
 During development, we first select a baseline system, consisting of a feature set of lexical features (word forms and lemmas) and a classifier, that we will compare the other results to.
-Next, we will test different combinations of the lexical feature sets from the baseline.
-We will then introduce more linguistic features, both morphosyntactic and semantic, as bags of features, and as backoff from word form $n$-grams.
-Lastly we will evaluate the inclusion of dependency triples, using both word form triples, and dependency triples with feature backoff.
+Next, we will test different combinations of the lexical feature sets used in the baseline testing.
+We will then introduce more linguistic features, both morphosyntactic and lexical semantic, as bags of features, and as backoff from word form $n$-grams.
+Finally, we will evaluate the inclusion of dependency triples, using both word form triples, and dependency triples with feature backoff.
 
@@
   \end{center}
-  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).
+  \caption{Results for baseline system; F-score for bag-of lexical features (word form and lemma), and bigram and trigram templates over word forms .
 MaxEnt is the MaximumEntropy classifier, SVM is the support vector machine, and RF is the RandomForest classifier.}
@@
 
-Table \ref{tab:baseline} shows baseline results in terms of F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma) for the three different classifiers.
-The presented results constitute the best F-scores after tuning, as discussed above.
+Table \ref{tab:baseline} shows baseline results in terms of F-score for bag-of lexical features (word form and lemma), and bigram and trigram templates over word form, for the three different classifiers.
 The overall best result came from the MaxEnt classifier with the bag of word form feature set.
-Generally, we see that feature sets containing bag of lexical features in some form outperform the $n$-gram feature sets.
+Generally, we see that feature sets containing bag of lexical features outperform the $n$-gram feature sets.
 The feature set we will use as a baseline in the next stage of our experiments is bag of word forms.
@@
 
-      $n$-gram combination & BoW & BoW \& BoL \\
+      $n$-gram combination & BoW & BoW+BoL \\
       \midrule
@@
       trigrams & $0.6180$ & $0.6453$ \\
-      $n$-grams & $0.6337$ & $\textbf{0.6656}$ \\
+      bi- and trigrams & $0.6337$ & $\textbf{0.6656}$ \\
       \bottomrule
@@
   \end{center}
-  \caption{F-scores of the bag of words feature sets, combined with word form bigrams, trigrams or both (termed simply $n$-grams in the table).}
+  \caption{F-scores of the bag of words, and bag of words and lemma feature sets, combined with word form bigrams, trigrams or both.}
   \label{tab:ngrams}
@@
 
-Now we test word form $n$-grams with bag of lexical features.
-As seen in table \ref{tab:ngrams}, we test bag of words alone, and bag of words with bag of lemmas, combined with the word form variants of bigrams, trigrams and both.
+We go on to test word form $n$-grams with bag of lexical features.
+As seen in Table \ref{tab:ngrams}, we test bag of words alone, and bag of words with bag of lemmas, combined with the word form variants of bigrams, trigrams and both.
 The best result without bag of lemmas comes from bag of words with only bigrams, with an F-score of $0.6376$, closely followed by bag of words with both types of $n$-grams, which got an F-score of $0.6337$.
-The best overall result, by far, came from the combination of bag of words, bag of lemmas, and both types of $n$-grams, which got an F-score of $0.6656$.
+The best result overall came from the combination of bag of words, bag of lemmas, and both types of $n$-grams, which got an F-score of $0.6656$.
 
 Next, we add the different feature types.
-We first use the bag of features feature template, for each feature, both on its own, and in a feature set with bag of word forms.
-As seen in table \ref{tab:bagOfFeatures}, none of the feature types alone result in higher F-scores than bag of words.
-However, all feature types but the POS, combined with bag of words, perform better than bag of words alone, with the combination of bag of lemmas and bag of words performing best, with an F-score of $0.6278$.
+We use the bag-of feature template, and for each feature, test both the bag of features on its own, and with bag of words.
+As seen in Table \ref{tab:bagOfFeatures}, none of the feature types alone result in higher F-scores than bag of words.
+However, all feature types (except the lexicalized POS-tags), combined with bag of words, perform better than bag of words alone.
+Though none of them beat bag of words and lemmas combined, with an F-score of $0.6278$.
 
@@
 
-      & bigram+ & trigram+ & $n$-gram+ \\
+      & bigram & trigram & bi+trigram \\
       \midrule
-      Lemma & $0.6611$ & $0.6480$ &  $\textbf{0.6649}$ \\ 
-      POS & $\textbf{0.6410}$ & $0.6294$ & $0.6320$ \\
-      Dep & $0.6208$ & $0.6194$ & $\textbf{0.6220}$ \\
-      Synset & $0.6454$ & $0.6448$ &  $\textbf{0.6537}$\\
-      Brown & $0.6285$ &  $0.6173$  & $\textbf{0.6335}$\\
+      Lemma backoff & $0.6611$ & $0.6480$ &  $\textbf{0.6649}$ \\ 
+      POS backoff & $\textbf{0.6410}$ & $0.6294$ & $0.6320$ \\
+      Dep backoff & $0.6208$ & $0.6194$ & $\textbf{0.6220}$ \\
+      Synset backoff & $0.6454$ & $0.6448$ &  $\textbf{0.6537}$\\
+      Brown backoff & $0.6285$ &  $0.6173$  & $\textbf{0.6335}$\\
 
@@
   \end{center}
-  \caption{Bag of words, bag of features and different combinations of $n$-grams with feature backoff. Each backoff combination is the one that achieved the best result.}
+  \caption{Backoff from different combinations of $n$-grams. The models also contain bag of words, and bag of features. Each backoff combination is the one that achieved the best result.}
   \label{tab:ngrambackoff}
@@
 
-Next we combine the results of bag of features, and $n$-grams, with $n$-gram feature backoffs.
-In table \ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the result of including backoff features.
+Next, we combine the results of bag of features, and $n$-grams, with $n$-gram feature backoffs.
+In Table \ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the results without backoff features.
+We test all possible backoff combinations.
 
@@
   \end{center}
-  \caption{Simple is the feature set containing Bag of Words and dependency triples.
-Combined is the feature set containing Bag of Words, bag of Lemmas, bigrams, trigrams and dependency triples.
+  \caption{Dependency triples with and without feature backoff.
+Simple is the feature set containing bag of words and dependency triples.
+Combined is the feature set containing bag of words, bag of lemmas, bigrams, trigrams and dependency triples.
 Each row backs off to a different feature type.}
@@
 The results reported are the backoff variant that acheived the best results.
-As seen in  table \ref{tab:depbackoff}, the inclusion of word form dependency triples improved upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for bag of words alone.
-Dependency triples did not, however, improve upon the results achieved by our best model, as the model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
+As seen in Table \ref{tab:depbackoff}, the inclusion of word form dependency triples improved upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for bag of words alone.
+Dependency triples did not, however, improve upon the results achieved by our best model, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
 
@@
 
-Our final model is the model consisting of bag of word forms, bag of lemmas, and word form bigrams and trigrams, which got the best result, with an F-score of $0.6656$.
-In subsection \ref{sec:heldout} we will also test that same model with the addition of bigram backoff to lemmas, which got an F-score of $0.6649$.
+Our final model (which we refer to as ``Combined'') is the model consisting of bag of word forms, bag of lemmas, and word form bigrams and trigrams, which got the best result, with an F-score of $0.6656$.
+In Subsection \ref{sec:heldout} we will also test that same model with the addition of trigram backoff to lemmas, which got an F-score of $0.6649$.
 
@@
 
-Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set.
-Our best model is the feature sets containing bag of words, bag of lemmas, and word form bigrams and trigrams.
-As seen in table \ref{tab:positives}, our classification of the development set using the best model resulted in $646$ true positives, $192$ false positives, and $457$ false negatives.
-This results in a precision of $0.7709$, and a recall of $0.5857$.
+%% Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set. 
+The combined feature set acheived a precision of $0.7709$, and a recall of $0.5857$.
 Compared with our baseline system, which had a precision of $0.6777$, and a recall of $0.5585$, we see that the majority of the improvement over the baseline comes from the increase in precision.
+When reviewing a random subsample of the false positives and false negatives, we see that the noisy data has caused some problems for the preprocessor.
+Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context.
 
-\begin{table}
-  \begin{center}
-    \begin{tabular}{llrr}
-      \toprule
+%% \begin{table}
+%%   \begin{center}
+%%     \begin{tabular}{llrr}
+%%       \toprule
 
-      & & Actual & \\
-      &  & Positive & Negative\\
-      \midrule
-      Predicted & Positive & $646$ & $192$ \\
-      & Negative & $457$ & $21,663$ \\
+%%       & & Actual & \\
+%%       &  & Positive & Negative\\
+%%       \midrule
+%%       Predicted & Positive & $646$ & $192$ \\
+%%       & Negative & $457$ & $21,663$ \\
 
-      \bottomrule
+%%       \bottomrule
 
-    \end{tabular}
-  \end{center}
-  \caption{The true and false, positives and negatives of our best model, when classifying the development set.
+%%     \end{tabular}
+%%   \end{center}
+%%   \caption{The true and false, positives and negatives of our best model, when classifying the development set.
 The numbers are the sum of each of the 10 classification, when performing 10-fold cross-validation.}
-  \label{tab:positives}
-\end{table}
-
-When reviewing a random subsample of the false positives and false negatives, we see that the noisy data has caused some problems for the preprocessor.
-Another source of errors, specifically false positives, are comments which use multiple typically threatening words in a non-threatening context.
+%%   \label{tab:positives}
+%% \end{table}
 
@@
 We performed our final testing on the held-out test set using the baseline feature set, the combined feature set, and the combined features set with trigram backoff using lemma features.
-As seen in table \ref{tab:heldout}, the both the best feature set, and the second best, from our development testing outperformed the baseline feature set.
+As seen in Table \ref{tab:heldout}, both the best feature set, and the second best, from our development testing, outperformed the baseline feature set.
 The best feature set from development also outperformed the second best.
-The difference in F-score was not as large as in our development testing, however.
-This may be due to the fact that the baseline performed a lot better in the held-out testing compared to the development testing, with an F-score of $0.6562$.
+The difference in F-scores between the baseline and the best feature set was not as large as in our development testing.
+However, this may be due to the fact that the baseline performed a lot better in the held-out testing compared to the development testing, with an F-score of $0.6562$.
 The F-scores of the combined feature sets were $0.6860$ and $0.6799$.
@@
       Baseline & $0.7325$ & $0.5943$ & $0.6562$ \\
-      Combined & $0.7532$ & $0.6299$ & $0.6860$  \\
-      Combined+ & $0.7703$ & $0.6085$ & $0.6799$ \\
+      Combined & $0.7532$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
+      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\
 
@@
 
-\section{Conclusion}
-\label{sec:disc}
+%% \section{Conclusion}
+%% \label{sec:disc}
 

### 2016-03-30 submission.tex
Changed formatting of TeX code

@@
 \documentclass[11pt,letterpaper]{article}
+\usepackage[utf8]{inputenc}
 \usepackage{naaclhlt2016}
@@
 
-%\naaclfinalcopy % Uncomment this line for the final submission
+\naaclfinalcopy % Uncomment this line for the final submission
 \def\naaclpaperid{***} %  Enter the naacl Paper ID here
@@
 % For several authors from the same institution:
-% \author{Author 1 \and ... \and Author n \\
-%         Address line \\ ... \\ Address line}
+\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
+        University of Oslo \\ ... \\ Address line}
 % if the names do not fit well on one line use
@@
 % at the top, where <new height> can be something larger than 2.25in
-\author{Author 1\\
-	    XYZ Company\\
-	    111 Anywhere Street\\
-	    Mytown, NY 10000, USA\\
-	    {\tt author1@xyz.org}
-	  \And
-	Author 2\\
-  	ABC University\\
-  	900 Main Street\\
-  	Ourcity, PQ, Canada A1A 1T2\\
-  {\tt author2@abc.ca}}
+%% \author{Aksel Wester\\
+%%   University of Oslo\\
+%%   111 Anywhere Street\\
+%%   Mytown, NY 10000, USA\\
+%%   {\tt aksellw@ifi.uio.no}
+%%   \And
+%%   Lilja Øvrelid\\
+%%   University of Oslo\\
+%%   900 Main Street\\
+%%   Ourcity, PQ, Canada A1A 1T2\\
+%%   {\tt liljao@ifi.uio.no}
+%%   \And
+%%   Erik Velldal\\
+%%   University of Oslo\\
+%%   900 Main Street\\
+%%   Ourcity, PQ, Canada A1A 1T2\\
+%%   {\tt erikve@ifi.uio.no}}
 
@@
 \begin{abstract}
-This article investigates the effect of various types of linguistic
-features (lexical, morphosyntactic and lexical semantic) for the task of
-detecting threats of violence in a data set of YouTube comments. It
-further examines the use of these features in combination with
-different representations of linguistic context, and feature backoff.
+This article investigates the effect of various types of linguistic features (lexical, morphosyntactic and lexical semantic) for the task of detecting threats of violence in a corpus of YouTube comments.
+It further examines the use of these features in combination with different representations of linguistic context, and feature backoff.
 Our results show that combinations of lexical features outperform the use of more complex syntactic and semantic features for this task.
@@
 \label{sec:intro}
-Threats of violence constitute an increasingly common occurrence in online
-discussions. It disproportionally affects women and minorities, often
-to the point of effectively eliminating them from taking part in
-discussions online. Moderators of social networks operate on such a
-large scale that manually reading all posts is an insurmountable
-task. Methods for automatically detecting threats could therefore
-potentially be very helpful, both to moderators of social networks,
-and to the members of those networks.
+Threats of violence constitute an increasingly common occurrence in online discussions.
+It disproportionally affects women and minorities, often to the point of effectively eliminating them from taking part in discussions online.
+Moderators of social networks operate on such a large scale that manually reading all posts is an insurmountable task.
+Methods for automatically detecting threats could therefore potentially be very helpful, both to moderators of social networks, and to the members of those networks.
 
-In this article, we evaluate different types of features for the task
-of detecting threats of violence in YouTube comments. We draw on both
-lexical, morphosyntactic and lexical semantic information sources and
-experiment with different machine learning algorithms. Our results
-indicate that successful detection of threats of violence is largely
-determined by lexical information.
+In this article, we evaluate different types of features for the task of detecting threats of violence in YouTube comments.
+We draw on both lexical, morphosyntactic and lexical semantic information sources and experiment with different machine learning algorithms.
+Our results indicate that successful detection of threats of violence is largely determined by lexical information.
 
@@
 \label{sec:prev}
-There is little previous work specifically devoted to the detection of
-threats of violence in text, however, there is previous work which
-examines other types of closely related phenomena, such as
-cyberbullying and hate-speech.
+There is little previous work specifically devoted to the detection of threats of violence in text, however, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.
 
-\newcite{dinakar2011} propose a method for the detection of
-cyberbullying by targeting combinations of profane or negative words,
-and words related to several predetermined sensitive topics. Their
-data set consists of over 50,000 YouTube comments taken from videos
-about controversial topics. %% They adopt a two-stage approach, where the
+\newcite{dinakar2011} propose a method for the detection of cyberbullying by targeting combinations of profane or negative words, and words related to several predetermined sensitive topics.
+Their data set consists of over 50,000 YouTube comments taken from videos about controversial topics.
+%% They adopt a two-stage approach, where the
 %% first stage consists of using a lexicon of negative words and a list
@@
 %% from each category as features.
-The experiments reported accuracies from 0.63 to 0.80, but did not
-report precision or recall.
+The experiments reported accuracies from 0.63 to 0.80, but did not report precision or recall.
 % lists of negative and profane words
@@
 
-There has been quite a bit of work focused on the detection of threats
-in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000
-threatening tweets collected by a website. In addition, a large number of random tweets were collected for
-development and testing. %% A set of 2.3 million random tweets was used
+There has been quite a bit of work focused on the detection of threats in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000 threatening tweets collected by a website.
+In addition, a large number of random tweets were collected for development and testing.
+%% A set of 2.3 million random tweets was used
 %% for development, and a set of 1 million was used for testing.
-The system relies on manually constructed recognition patterns, in the
-form of n-grams 
+The system relies on manually constructed recognition patterns, in the form of n-grams 
 %(uni-, bi- and trigrams, as well as skip bi- and trigrams)
-, but do not go into detail about the methods used to
-construct these patterns%% , stating that the researchers relied on their
+, but do not go into detail about the methods used to construct these patterns%% , stating that the researchers relied on their
 %% (linguistic) intuition as speakers of Dutch \cite{nellngram2013}
-. In
-\newcite{nellshallow2013}, a manually crafted shallow parser is added
-to the system. This improves results to a precision of 0.39 and a
-recall of 0.59.
+. In \newcite{nellshallow2013}, a manually crafted shallow parser is added to the system. This improves results to a precision of 0.39 and a recall of 0.59.
 % handcrafted patterns
@@
 
-\newcite{warner2012} present a method for detecting hate speech in
-user-generated web text from the internet, which relies on machine
-learning in combination with template-based features. The task
-is approached as a word-sense disambiguation task, since the same
-words can be used in both hateful and non-hateful contexts. The
-features used in the classification were combinations of uni-, bi- and
-trigrams, part-of-speech-tags and Brown clusters.  The best results of
-the classifications were obtained using only unigrams as features,
-with a precision of 0.67 and a recall of 0.60. The other feature
-sets garnered much lower results, and the authors suggest that deeper
-parsing could reveal significant phrase patterns.
+\newcite{warner2012} present a method for detecting hate speech in user-generated web text from the internet, which relies on machine learning in combination with template-based features.
+The task is approached as a word-sense disambiguation task, since the same words can be used in both hateful and non-hateful contexts.
+The features used in the classification were combinations of uni-, bi- and trigrams, part-of-speech-tags and Brown clusters.
+The best results of the classifications were obtained using only unigrams as features, with a precision of 0.67 and a recall of 0.60.
+The other feature sets garnered much lower results, and the authors suggest that deeper parsing could reveal significant phrase patterns.
 % only unigrams best results
@@
 
-Perhaps closest to the current work is the work of
-\newcite{hammer2014}, which reports on an experiment on the same data set that
-we will be using in our own experiments. The method uses a logistic
-LASSO regression analysis on bigrams (skip-grams) of important words
-to classify sentences as either \tovs{} or not.  The system makes use of a
-list of words that are correlated with threats of violence. The
-article does not, however, describe exactly how these important words
-were selected, stating only that words were chosen that were
-significantly correlated with the response (violent/non-violent
-sentence). Results are reported only in terms of proportion of false
-positives for the two classes, and it is not clear how the data was
-split for training and evaluation. This makes it difficult to compare our results to those of \newcite{hammer2014}.
+Perhaps closest to the current work is the work of \newcite{hammer2014}, which reports on an experiment on the same corpus that we will be using in our own experiments.
+The method uses a logistic LASSO regression analysis on bigrams (skip-grams) of important words to classify sentences as either \tovs{} or not.
+The system makes use of a list of words that are correlated with threats of violence.
+The article does not, however, describe exactly how these important words were selected, stating only that words were chosen that were significantly correlated with the response (violent/non-violent sentence).
+Results are reported only in terms of proportion of false positives for the two classes, and it is not clear how the data was split for training and evaluation.
+This makes it difficult to compare our results to those of \newcite{hammer2014}.
 
-\section{The YouTube threat data set}
+\section{The YouTube threat corpus}
 \label{sec:data}
-The YouTube threat data set is comprised of user-written comments from
-eight different YouTube videos \cite{hammer2014}. A comment
-consists of a set of sentences, each of them manually annotated to be
-either a \tov{} (or support for a \tov{}), or not. The data set
-furthermore records the username
+The YouTube threat corpus is comprised of user-written comments from eight different YouTube videos \cite{hammer2014}.
+A comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not.
+The corpus furthermore records the username
 %% \footnote{In 2013, YouTube changed its
@@
 %%   only be identified by their usernames.}
-  of the user that posted the
-comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
-Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
+  of the user that posted the comment.
+The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc.
+\cite{hammer2014}.
 %The videos cover slightly different topics, the videos all contain the same
@@
 
-The data set consists of 9,845 comments, comprised of 28,643
-sentences, see Table \ref{tab:dataset}.
+The corpus consists of 9,845 comments, comprised of 28,643 sentences, see Table \ref{tab:dataset}.
 %% In total there are 402,673 tokens in the sentences in the data set.
-There are 1,285 comments
-containing threats, and 1,384 sentences containing threats, as seen in
-Table \ref{tab:dataset}.  \newcite{hammer2014} reports inter-annotator
-agreement on this data set to be 98~\%, as calculated on 120 of the
-comments, doubly annotated for evaluation.
+There are 1,285 comments containing threats, and 1,384 sentences containing threats, as seen in Table \ref{tab:dataset}.
+\newcite{hammer2014} reports inter-annotator agreement on this data set to be 98~\%, as calculated on 120 of the comments, doubly annotated for evaluation.
 
@@
 %to-do: should we anonymize the user names?
-Figure \ref{fig:comments} provides some examples of comments containing
-\tovs{} taken from the data set. The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
+Figure \ref{fig:comments} provides some examples of comments containing \tovs{} taken from the corpus.
+The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
 %% An empty line indicates the end of a comment.
-The sentences are annotated
-with a number indicating whether they contain a \tov{} (1), or not
-(0).
+The sentences are annotated with a number indicating whether they contain a \tov{} (1), or not (0).
 
@@
 \end{Verbatim}
-\caption{Examples of comments from the data set.}
+\caption{Examples of comments from the YouTube threat corpus.}
 \label{fig:comments}
@@
 \label{sec:exp}
-Much of the previous work presented in Section \ref{sec:prev} made use of
-precompiled lists of correlated words and manually crafted
-patterns. Whereas these resources can be effective, they are highly
-task-specific and do not easily lend themselves to replication.  The
-previous work further highlights the effectiveness of lexical features
-(word-based features), however, several of the authors suggest that parsing
-may be beneficial for these tasks.
+Much of the previous work presented in Section \ref{sec:prev} made use of precompiled lists of correlated words and manually crafted patterns.
+Whereas these resources can be effective, they are highly task-specific and do not easily lend themselves to replication.
+The previous work further highlights the effectiveness of lexical features (word-based features), however, several of the authors suggest that parsing may be beneficial for these tasks.
 
-In this work we experiment with a wide range of linguistic features in our system and investigate the introduction of
-linguistic context through a set of feature templates. We also
-generalize these features through a backoff technique. Throughout, we
-make use of resources and tools that are freely available and reusable in order
-to construct our system.
+In this work we experiment with a wide range of linguistic features in our system and investigate the introduction of linguistic context through a set of feature templates.
+We also generalize these features through a backoff technique.
+Throughout, we make use of resources and tools that are freely available and reusable in order to construct our system.
 
@@
 
-\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the data
-set has been manually split into sentences as part of the annotation
-process.  We performed tokenization, lemmatization, PoS-tagging and
-dependency parsing using the SpaCy
-toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard
-Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more
-coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
-dependency parser assigns an analysis in compliance with the ClearNLP
-converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example
-dependency graph from the data set. The data set was further enriched
-with the cluster labels described in Turian et
-al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering
-algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
-corpus containing Reuters English newswire text.
+\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the corpus has been manually split into sentences as part of the annotation process.
+We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the SpaCy toolkit\footnote{https://spacy.io/}.
+SpaCy assigns both the standard Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}.
+The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example dependency graph from the corpus.
+The corpus was further enriched with the cluster labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a corpus containing Reuters English newswire text.
 %, with approximately 63 million words and 3.3 million sentences.
-We vary the number of
-clusters to be either 100, 320, 1000 or 3200 clusters and use the full
-cluster label.  We also make use of the WordNet resource
-\cite{wordnet} to determine a word's synset, parent and grandparent
-synset.
+We vary the number of clusters to be either 100, 320, 1000 or 3200 clusters and use the full cluster label.
+We also make use of the WordNet resource \cite{wordnet} to determine a word's synset, parent and grandparent synset.
 
@@
 \end{dependency}
-\caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
+\caption{Dependency parse of example sentence from the corpus, with assigned uPOS tags.}
 \label{fig:dep}
@@
 \paragraph{Features}
-Based on the enriched data set, as described above, we experiment with the following feature types:
+Based on the enriched corpus, as described above, we experiment with the following feature types:
 
@@
 %% \end{description}
-These features are structured according to a set of \emph{feature
-  templates}, which introduce varying degrees of linear order and
-syntactic context: bag-of-features (unordered), bigrams, trigrams and
-dependency triples. These feature templates are applied to the feature
-types presented above, in order to yield features like the following
-for our examples sentence in Figure \ref{fig:dep}:
+These features are structured according to a set of \emph{feature templates}, which introduce varying degrees of linear order and syntactic context: bag-of-features (unordered), bigrams, trigrams and dependency triples.
+These feature templates are applied to the feature types presented above, in order to yield features like the following for our examples sentence in Figure \ref{fig:dep}:
 
@@
 \end{itemize}
-Our lexical features are very specific and require the exact
-combination of two lexical items in order to apply to a new instance.
-Following \newcite{Jos:Pen:2009}, we therefore experiment with
-generalization of features by backoff to a more general category,
-e.g. from word form to lemma or PoS. A dependency triple over word
-forms like $<$kill, dobj, them$>$ would thus be generalized to
-$<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj,
-PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
-trigram and dependency triple features.
+Our lexical features are very specific and require the exact combination of two lexical items in order to apply to a new instance.
+Following \newcite{Jos:Pen:2009}, we therefore experiment with generalization of features by backoff to a more general category, e.g.
+from word form to lemma or PoS.
+A dependency triple over word forms like $<$kill, dobj, them$>$ would thus be generalized to $<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj, PRON$>$ using \emph{modifier-backoff}.
+We apply backoff to bigram, trigram and dependency triple features.
 

### 2016-03-30 submission.tex
Made changes discussed in last meeting

@@
 \author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
-        University of Oslo \\ ... \\ Address line}
+  Department of Informatics \\
+  University of Oslo, Norway \\
+  ... \\
+  \{aksellw, liljao, erikve\}@ifi.uio.no}
 % if the names do not fit well on one line use
@@
 
+We use a simple count-based feature reduction on the features in each feature set, where we include in the feature set only the features the appear at least twice in the training data.
+
 \subsection{Development results}
@@
   \end{center}
-  \caption{F-scores of the bag of words, and bag of words and lemma feature sets, combined with word form bigrams, trigrams or both.}
+  \caption{F-scores of the bag of words feature set, with different combinations of the other feature sets tested in Table \ref{tab:baseline}.}
   \label{tab:ngrams}
@@
   \end{center}
-  \caption{Results of bag of feature variations with different feature types. The results shown are the F-scores of each feature set after tuning, using the MaxEnt classifier.}
+  \caption{F-scores of bag of features (BoF) with and without bag of words (BoW).
+POS\textsubscript{Lex} and Dep\textsubscript{Lex} are lexicalized POS and dep-tags, respectively, where each feature is a tuple consisting of the tag and the word form of the token.}
   \label{tab:bagOfFeatures}

### 2016-03-30 submission.tex
misc smaller adjustments

@@
 \title{Features for detecting threats of violence in YouTube comments}
-%\title{Detecting threats of violence in YouTube comments}
+%\title{Online threat detection}
+%\title{Threat detection for online comments}
+%\title{Detecting threats of violence in online comments}
+%\title{Detecting violent threats online}
 
@@
   University of Oslo, Norway \\
-  ... \\
   \{aksellw, liljao, erikve\}@ifi.uio.no}
@@
 \begin{abstract}
-This article investigates the effect of various types of linguistic features (lexical, morphosyntactic and lexical semantic) for the task of detecting threats of violence in a corpus of YouTube comments.
+This paper investigates the effect of various types of linguistic features (lexical, syntactic and semantic) for the task of detecting threats of violence in a corpus of YouTube comments.
 It further examines the use of these features in combination with different representations of linguistic context, and feature backoff.
@@
 Moderators of social networks operate on such a large scale that manually reading all posts is an insurmountable task.
-Methods for automatically detecting threats could therefore potentially be very helpful, both to moderators of social networks, and to the members of those networks.
+Methods for automatically detecting threats could therefore potentially be very helpful, both to moderators of social networks, and to their members.
 
@@
 
-There has been quite a bit of work focused on the detection of threats in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000 threatening tweets collected by a website.
-In addition, a large number of random tweets were collected for development and testing.
-%% A set of 2.3 million random tweets was used
+There has been quite a bit of work focused on the detection of threats in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000 threatening tweets.
+% collected by a website.
+In addition, a large number of random tweets were collected for development and testing. %% A set of 2.3 million random tweets was used
 %% for development, and a set of 1 million was used for testing.
-The system relies on manually constructed recognition patterns, in the form of n-grams 
+The system relies on manually constructed recognition patterns in the form of n-grams, 
 %(uni-, bi- and trigrams, as well as skip bi- and trigrams)
-, but do not go into detail about the methods used to construct these patterns%% , stating that the researchers relied on their
+but details about the methods used to construct these patterns are not given.%% , stating that the researchers relied on their
 %% (linguistic) intuition as speakers of Dutch \cite{nellngram2013}
-. In \newcite{nellshallow2013}, a manually crafted shallow parser is added to the system. This improves results to a precision of 0.39 and a recall of 0.59.
+In \newcite{nellshallow2013}, a manually crafted shallow parser is added to the system. This improves results to a precision of 0.39 and a recall of 0.59.
 % handcrafted patterns
@@
 \begin{table}
+  \begin{smaller}
     \begin{center}
       \begin{tabular}{lrrr}
-  %&   &   &   \\
+        % & & & \\
         \toprule
@@
       \end{tabular}
-\end{center}
       \caption{Number of comments, sentences and users in \ds{}.}
       \label{tab:dataset}
+    \end{center}
+  \end{smaller}
 \end{table}
@@
 In this work we experiment with a wide range of linguistic features in our system and investigate the introduction of linguistic context through a set of feature templates. 
-We also generalize these features through a backoff technique.
-Throughout, we make use of resources and tools that are freely available and reusable in order to construct our system.
+% fixme: det virker litt rart å skille mellom trekk og lingvistisk kontekst? 
+We also generalize these features through a backoff technique. Throughout, we make use of resources and tools that are freely available and reusable in order to construct our system.
 
@@
 
-We test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a RandomForest classifier (RF).
+We test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a Random Forest classifier (RF).
 We approach the task as a binary classification task, and we use scikit-learn \cite{scikit-learn} for our classification.
@@
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
-When tuning the RandomForest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
+When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
 In the following experiments, we perform tuning on all feature sets.
@@
 Our lexical features are very specific and require the exact combination of two lexical items in order to apply to a new instance.
-Following \newcite{Jos:Pen:2009}, we therefore experiment with generalization of features by backoff to a more general category, e.g.
-from word form to lemma or PoS.
-A dependency triple over word forms like $<$kill, dobj, them$>$ would thus be generalized to $<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj, PRON$>$ using \emph{modifier-backoff}.
-We apply backoff to bigram, trigram and dependency triple features.
+Following \newcite{Jos:Pen:2009}, we therefore experiment with generalizing features by `backing off' to a more general category, e.g., from word form to lemma or PoS.
+For example, a dependency triple over word forms like $<$kill, dobj, them$>$ would thus be generalized to $<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj, PRON$>$ using \emph{modifier-backoff}.
+These additional backoff features are included for bigrams and trigrams as well as dependency triples.
 
@@
 \begin{table}
+  \begin{smaller}
     \begin{center}
@@
     \end{center}
-  \caption{Results for baseline system; F-score for bag-of lexical features (word form and lemma), and bigram and trigram templates over word forms .
-MaxEnt is the MaximumEntropy classifier, SVM is the support vector machine, and RF is the RandomForest classifier.}
+    \caption{Results for baseline system; F-score for bag-of lexical features
+      (word form and lemma), and bigram and trigram templates over word
+      forms. From left to right the columns correspond to Maximum Entropy
+      classifiers, Support Vector Machines, and Random Forests.}
     \label{tab:baseline}
+  \end{smaller}
 \end{table}
@@
     \end{center}
-  \caption{F-scores of the bag of words feature set, with different combinations of the other feature sets tested in Table \ref{tab:baseline}.}
+    \caption{F-scores of the bag of words feature set, with different
+      combinations of the other feature sets tested in Table
+      \ref{tab:baseline}.}
     \label{tab:ngrams}
     % tidligere Tabell 4
+  \end{smaller}
 \end{table}
@@
 \begin{table}
+  \begin{smaller}    
   \begin{center}
@@
   % tidligere Tabell 3
+  \end{smaller}
 \end{table}
@@
       %% \\ % synset reg, b320
-
       & bigram & trigram & bi+trigram \\
@@
   \label{tab:ngrambackoff}
+  \end{smaller}
 \end{table}
@@
       \toprule           
-
       Dependency backoff & Simple & Combined\\
@@
       Brown & $0.6299$ & $0.6504$ \\ % 1. Brown 320, 2. Brown 1000                 
-
       \bottomrule
-
     \end{tabular}
@@
   \label{tab:depbackoff}
+  \end{smaller}
 \end{table}
@@
 \begin{table}
+\begin{smaller}
   \begin{center}
@@
       \toprule      
-
       & Precision & Recall & F-score\\
@@
       Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            
-
       \bottomrule
-
     \end{tabular}
@@
   \label{tab:heldout}
+\end{smaller}
 \end{table}
 
-%% \section{Conclusion}
-%% \label{sec:disc}
+\section{Conclusion}
+\label{sec:conclusion}
 

### 2016-03-31 submission.tex
misc changes to sections 0-2

@@
 
-\title{Features for detecting threats of violence in YouTube comments}
+% \title{Features for detecting threats of violence in YouTube comments}
+\title{Threat detection in online discussions}
 %\title{Online threat detection}
@@
 \begin{abstract}
-This paper investigates the effect of various types of linguistic features (lexical, syntactic and semantic) for the task of detecting threats of violence in a corpus of YouTube comments.
-It further examines the use of these features in combination with different representations of linguistic context, and feature backoff.
+This paper investigates the effect of various types of linguistic features (lexical, syntactic and semantic) for training classifiers to detect threats of violence in a corpus of YouTube comments.
+% It further examines the use of these features in combination with different representations of linguistic context, and feature backoff.
 Our results show that combinations of lexical features outperform the use of more complex syntactic and semantic features for this task.
@@
 Moderators of social networks operate on such a large scale that manually reading all posts is an insurmountable task.
-Methods for automatically detecting threats could therefore potentially be very helpful, both to moderators of social networks, and to their members.
+Methods for automatically detecting threats could therefore potentially be very helpful, both to moderators of social networks and to their members.
 
@@
 \label{sec:prev}
-There is little previous work specifically devoted to the detection of threats of violence in text, however, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.
+There is little previous work specifically devoted to the detection of threats of violence in text.
+However, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.
 
@@
 %(uni-, bi- and trigrams, as well as skip bi- and trigrams)
-but details about the methods used to construct these patterns are not given.%% , stating that the researchers relied on their
+but details about the strategy used to construct these patterns are not given. %% , stating that the researchers relied on their
 %% (linguistic) intuition as speakers of Dutch \cite{nellngram2013}
@@
 
-\newcite{warner2012} present a method for detecting hate speech in user-generated web text from the internet, which relies on machine learning in combination with template-based features.
+\newcite{warner2012} present a method for detecting hate speech in user-generated web text, which relies on machine learning in combination with template-based features.
 The task is approached as a word-sense disambiguation task, since the same words can be used in both hateful and non-hateful contexts.
 The features used in the classification were combinations of uni-, bi- and trigrams, part-of-speech-tags and Brown clusters.
-The best results of the classifications were obtained using only unigrams as features, with a precision of 0.67 and a recall of 0.60.
+The best results were obtained using only unigram features, with a precision of 0.67 and a recall of 0.60.
 The other feature sets garnered much lower results, and the authors suggest that deeper parsing could reveal significant phrase patterns.
@@
 
-Perhaps closest to the current work is the work of \newcite{hammer2014}, which reports on an experiment on the same corpus that we will be using in our own experiments.
+Most closely related to the current paper is the work of \newcite{hammer2014}, reporting on experiments on (a previous version of) the same corpus as used here.
 The method uses a logistic LASSO regression analysis on bigrams (skip-grams) of important words to classify sentences as either \tovs{} or not.
@@
 The article does not, however, describe exactly how these important words were selected, stating only that words were chosen that were significantly correlated with the response (violent/non-violent sentence).
-Results are reported only in terms of proportion of false positives for the two classes, and it is not clear how the data was split for training and evaluation.
-This makes it difficult to compare our results to those of \newcite{hammer2014}.
+Results are reported only in terms of proportion of false positives for the two classes, and it is not clear how the data was split for training and evaluation, making it difficult to directly compare our results to those of \newcite{hammer2014}.
 

### 2016-03-31 submission.tex
changes to sec. 3

@@
 \label{sec:data}
-The YouTube threat corpus is comprised of user-written comments from eight different YouTube videos \cite{hammer2014}.
-A comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not.
-The corpus furthermore records the username
+The YouTube threat corpus comprises user-written comments from eight different YouTube videos \cite{hammer2014}.
+The videos cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc.
+\cite{hammer2014}.
+%The videos cover slightly different topics, the videos all contain the same
+%type of discussions, namely of xenophobia and racism. 
+A given comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not. The corpus also records the username
 %% \footnote{In 2013, YouTube changed its
@@
 %%   only be identified by their usernames.}
-  of the user that posted the comment.
-The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc.
-\cite{hammer2014}.
-%The videos cover slightly different topics, the videos all contain the same
-%type of discussions, namely of xenophobia and racism.
+  of the comment author.
 
-The corpus consists of 9,845 comments, comprised of 28,643 sentences, see Table \ref{tab:dataset}.
+As shown in Table~\ref{tab:dataset}, the corpus consists of 9,845 comments, comprising 28,643 sentences.
 %% In total there are 402,673 tokens in the sentences in the data set.
-There are 1,285 comments containing threats, and 1,384 sentences containing threats, as seen in Table \ref{tab:dataset}.
+There are 1,384 sentences containing threats, spread over 1,285 comments.
 \newcite{hammer2014} reports inter-annotator agreement on this data set to be 98~\%, as calculated on 120 of the comments, doubly annotated for evaluation.
@@
 %to-do: should we anonymize the user names?
-Figure \ref{fig:comments} provides some examples of comments containing \tovs{} taken from the corpus.
+Figure~\ref{fig:comments} provides some examples of comments containing \tovs{} taken from the corpus.
 The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
 %% An empty line indicates the end of a comment.
-The sentences are annotated with a number indicating whether they contain a \tov{} (1), or not (0).
+The sentences are annotated with a number indicating whether they contain a \tov{} (1) or not (0).
 
@@
 \end{Verbatim}
-\caption{Examples of comments from the YouTube threat corpus.}
+\caption{Example comments from the YouTube threat corpus.}
 \label{fig:comments}
@@
 \label{sec:exp}
-Much of the previous work presented in Section \ref{sec:prev} made use of precompiled lists of correlated words and manually crafted patterns.
+Much of the previous related work presented in Section~\ref{sec:prev} made use of precompiled lists of correlated words and manually crafted patterns.
 Whereas these resources can be effective, they are highly task-specific and do not easily lend themselves to replication.
-The previous work further highlights the effectiveness of lexical features (word-based features), however, several of the authors suggest that parsing may be beneficial for these tasks.
+Furthermore, while much of the previous work seem to highlight the effectiveness of lexical features, several of the authors also suggest that parsing may be beneficial for these tasks.
 
-In this work we experiment with a wide range of linguistic features in our system and investigate the introduction of linguistic context through a set of feature templates. 
-% fixme: det virker litt rart å skille mellom trekk og lingvistisk kontekst? 
-We also generalize these features through a backoff technique. Throughout, we make use of resources and tools that are freely available and reusable in order to construct our system.
+The approach followed in the current paper is to train a machine-learned model to automatically detect threaths, experimenting with a range of different sources of linguistic information for defining our feature templates.
+We also generalize these features through a `backoff' technique. Throughout, we make use of resources and tools that are freely available and reusable.
 

### 2016-03-31 submission.tex
endringer i seksjon 4

@@
 
-\section{Previous work}
+\section{Related work}
 \label{sec:prev}
@@
 \label{sec:data}
-The YouTube threat corpus comprises user-written comments from eight different YouTube videos \cite{hammer2014}.
+The YouTube threat corpus\footnote{Please contact the authors if you want to obtain access to the corpus for your own research.} comprises user-written comments from eight different YouTube videos \cite{hammer2014}.
 The videos cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc.
-\cite{hammer2014}.
 %The videos cover slightly different topics, the videos all contain the same
 %type of discussions, namely of xenophobia and racism. 
-A given comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not. The corpus also records the username
+A given comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not. The corpus also records usernames of the commenters.
 %% \footnote{In 2013, YouTube changed its
@@
 %%   only be identified by their usernames.}
-  of the comment author.
 
@@
 %to-do: should we anonymize the user names?
-Figure~\ref{fig:comments} provides some examples of comments containing \tovs{} taken from the corpus.
+Figure~\ref{fig:comments} provides some examples of comments from the corpus.
 The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
@@
 
-The approach followed in the current paper is to train a machine-learned model to automatically detect threaths, experimenting with a range of different sources of linguistic information for defining our feature templates.
+The approach followed in the current paper is to train a machine-learned model to automatically detect threaths.
+We experiment with a range of different sources of linguistic information for defining our feature templates.
 We also generalize these features through a `backoff' technique. Throughout, we make use of resources and tools that are freely available and reusable.
@@
 \paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the corpus has been manually split into sentences as part of the annotation process.
-We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the SpaCy toolkit\footnote{https://spacy.io/}.
+We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the spaCy NLP toolkit.
 SpaCy assigns both the standard Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}.
-The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example dependency graph from the corpus.
-The corpus was further enriched with the cluster labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a corpus containing Reuters English newswire text.
+The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure~\ref{fig:dep} for an example dependency graph from the corpus.
+The corpus was further enriched with the cluster labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced from the Reuters corpus of English newswire text (RCV1).
 %, with approximately 63 million words and 3.3 million sentences.
 We vary the number of clusters to be either 100, 320, 1000 or 3200 clusters and use the full cluster label.
-We also make use of the WordNet resource \cite{wordnet} to determine a word's synset, parent and grandparent synset.
+We also make use of the WordNet resource \cite{wordnet} to include information about the synset of a word, as well as its parent and grandparent synsets.
 
@@
 
-We test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a Random Forest classifier (RF).
-We approach the task as a binary classification task, and we use scikit-learn \cite{scikit-learn} for our classification.
+We test three different classification frameworks in our development testing: Maximum Entropy (MaxEnt), Support Vector Machines (SVM), and Random Forests (RF).
+We approach the task as a binary classification task, using the implementations found in the scikit-learn toolkit \cite{scikit-learn}.
 
 \paragraph{Tuning}
-When tuning each model, we aim to maximize the F-score of the model.
-In the MaxEnt classifier and SVM we tune the C-value, which for both classifiers is the inverse of regularization strength.
-When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with ever-decreasing increments, with the range of C-values centered on the best performing C-value thus far.
+When tuning each model, we aim to maximize the F-score.
+For the MaxEnt and SVM classifiers we tune the regularization parameter (C), where a smaller value corresponds to stronger regularization.
+When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with decreasing increments, with the range of C-values centered on the best performing C-value thus far.
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
@@
 \paragraph{Features}
-Based on the enriched corpus, as described above, we experiment with the following feature types:
+Based on the enriched corpus, as described above, we experiment with the following sources of information for defining our features:
 
@@
 
-We use a simple count-based feature reduction on the features in each feature set, where we include in the feature set only the features the appear at least twice in the training data.
+We impose a simple count-based reduction of the feature set; only features appearing at least twice in the training data are included in the model.
 

### 2016-03-31 submission.tex
en del endringer i siste halvdel, i tråd med møtet tidligere i dag

@@
 Threats of violence constitute an increasingly common occurrence in online discussions.
-It disproportionally affects women and minorities, often to the point of effectively eliminating them from taking part in discussions online.
+It disproportionately affects women and minorities, often to the point of effectively eliminating them from taking part in discussions online.
 Moderators of social networks operate on such a large scale that manually reading all posts is an insurmountable task.
@@
 There is little previous work specifically devoted to the detection of threats of violence in text.
-However, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.
+However, there is previous work which examines other types of closely related phenomena, such as `cyberbullying' and hate-speech.
 
@@
 %% for development, and a set of 1 million was used for testing.
-The system relies on manually constructed recognition patterns in the form of n-grams, 
+The system relies on manually constructed recognition patterns in the form of $n$-grams, 
 %(uni-, bi- and trigrams, as well as skip bi- and trigrams)
@@
 Figure~\ref{fig:comments} provides some examples of comments from the corpus.
-The first line is the annonymized username, and the subsequent lines are the sentences of the comment.
+The first line is the anonymized username, and the subsequent lines are the sentences of the comment.
 %% An empty line indicates the end of a comment.
@@
 \label{sec:exp}
-Much of the previous related work presented in Section~\ref{sec:prev} made use of precompiled lists of correlated words and manually crafted patterns.
+Much of the previous related work presented in Section~\ref{sec:prev} made use of pre-compiled lists of correlated words and manually crafted patterns.
 Whereas these resources can be effective, they are highly task-specific and do not easily lend themselves to replication.
@@
 
-The approach followed in the current paper is to train a machine-learned model to automatically detect threaths.
+The approach followed in the current paper is to train a machine-learned model to automatically detect threats.
 We experiment with a range of different sources of linguistic information for defining our feature templates.
@@
 \paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the corpus has been manually split into sentences as part of the annotation process.
-We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the spaCy NLP toolkit.
-SpaCy assigns both the standard Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}.
+We performed tokenization, lemmatization, POS-tagging and dependency parsing using the spaCy NLP toolkit.
+SpaCy assigns both the standard Penn Treebank POS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal POS tag set of \newcite{Pet:Das:McD:12}.
 The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure~\ref{fig:dep} for an example dependency graph from the corpus.
@@
   \item Penn Treebank (PTB) POS
-  \item Universal (uPOS) PoS
+  \item Universal POS (uPOS)
   \item Dependency Relation
@@
 %% \end{description}
-These features are structured according to a set of \emph{feature templates}, which introduce varying degrees of linear order and syntactic context: bag-of-features (unordered), bigrams, trigrams and dependency triples.
-These feature templates are applied to the feature types presented above, in order to yield features like the following for our examples sentence in Figure \ref{fig:dep}:
+The features are structured according to a set of \emph{feature templates}, which record varying degrees of linear order and syntactic context: \emph{bag-of} features (unordered), bigrams, trigrams and dependency triples.
+These feature templates are applied with the information sources presented above, yielding features like the following for our examples sentence in Figure~\ref{fig:dep}:
 
@@
 
-\item Depdendency triples: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, ... \}
+\item Dependency triples: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, ... \}
 \end{itemize}
-Our lexical features are very specific and require the exact combination of two lexical items in order to apply to a new instance.
-Following \newcite{Jos:Pen:2009}, we therefore experiment with generalizing features by `backing off' to a more general category, e.g., from word form to lemma or PoS.
+%<-- fixme: Hvis vi får plass kan vi kanskje legge til noen fler eksempler som bruker mer av den tilgjengelige informasjonen vi gjør et poeng av? F.eks n-grams av POS, synsets, lemma, osv?
+
+Our lexicalized features are very specific and require the exact combination of two lexical items in order to apply to a new instance.
+Following \newcite{Jos:Pen:2009}, we therefore experiment with generalizing features by `backing off' to a more general category, e.g., from word form to lemma or POS.
 For example, a dependency triple over word forms like $<$kill, dobj, them$>$ would thus be generalized to $<$VERB, dobj, them$>$ using \emph{head-backoff}, and $<$kill, dobj, PRON$>$ using \emph{modifier-backoff}.
@@
 
-During development, we first select a baseline system, consisting of a feature set of lexical features (word forms and lemmas) and a classifier, that we will compare the other results to.
-Next, we will test different combinations of the lexical feature sets used in the baseline testing.
-We will then introduce more linguistic features, both morphosyntactic and lexical semantic, as bags of features, and as backoff from word form $n$-grams.
-Finally, we will evaluate the inclusion of dependency triples, using both word form triples, and dependency triples with feature backoff.
+We start by defining an informed baseline system, empirically selecting an initial set of features and a classification framework to use as a basis and reference point for further development.
+The features for this initial round of tuning comprise basic lexical features; word forms and lemmas, in addition to $n$-grams defined over these.
+
+In the second round of experiments we test combinations of these basic lexical feature types, before moving on to introduce more linguistic features, both syntactic and semantic, as \emph{bag-of} features, and as backoff from word form $n$-grams.
+Finally, we will evaluate the inclusion of dependency triples.
+%, using both word form triples, and dependency triples with feature backoff.
 
@@
         Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
-        Bigrams & $0.4856$ & $0.4887$ & $0.4944$ \\
-        Trigrams & $0.2776$ & $0.2856$ & $0.2859$ \\
+        Bigrams of word forms & $0.4856$ & $0.4887$ & $0.4944$ \\
+        Trigrams of word forms & $0.2776$ & $0.2856$ & $0.2859$ \\
 
@@
 
-Table \ref{tab:baseline} shows baseline results in terms of F-score for bag-of lexical features (word form and lemma), and bigram and trigram templates over word form, for the three different classifiers.
-The overall best result came from the MaxEnt classifier with the bag of word form feature set.
-Generally, we see that feature sets containing bag of lexical features outperform the $n$-gram feature sets.
-The feature set we will use as a baseline in the next stage of our experiments is bag of word forms.
-The feature set recieved an F-score of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$, using the MaxEnt classifier after tuning.
-We will also be using only the MaxEnt classifier for the remainder of the feature set experiments.
+Table~\ref{tab:baseline} shows initial development results in terms of F-score for the the three different classifiers across four different feature sets; bags of word-forms and lemmas, as well as bigram and trigram over word forms.
+Generally, we see that feature sets containing lexical \emph{bag-of} features outperform the $n$-gram features.
+The overall best result came from the MaxEnt classifier with the bag-of-word form feature set.
+This model yielded an F-score of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$, using the MaxEnt classifier after tuning.
+This is the feature set we will use as our basic reference model in the next stage of our experiments is the bag-of-word forms.
+We will also only be using the the MaxEnt classifier for the remainder for reported development experiments.
+Not only did the MaxEnt model have the best performance for the basic BoW feature sets, but it is also the framework that is most convenient to use for exploring many combinations of features given that a MaxEnt model can be trained in much less time than an SVM or Random Forest classifier.
 
@@
         no $n$-grams & $0.6123$ & $0.6278$ \\
-        bigrams & $\textbf{0.6376}$ & $0.6577$ \\
-        trigrams & $0.6180$ & $0.6453$ \\
-        bi- and trigrams & $0.6337$ & $\textbf{0.6656}$ \\
+        +bigrams & $0.6376$ & $0.6577$ \\
+        +trigrams & $0.6180$ & $0.6453$ \\
+        +bi- and trigrams & $0.6337$ & $\textbf{0.6656}$ \\
         \bottomrule
@@
     \end{center}
-    \caption{F-scores of the bag of words feature set, with different
-      combinations of the other feature sets tested in Table
-      \ref{tab:baseline}.}
+    \caption{F-scores of the bag-of-words feature set, with different
+      combinations of the other feature sets tested in Table~\ref{tab:baseline}, namely bag-of-lemmas and $n$-grams of word forms.}
     \label{tab:ngrams}
@@
 
-We go on to test word form $n$-grams with bag of lexical features.
-As seen in Table \ref{tab:ngrams}, we test bag of words alone, and bag of words with bag of lemmas, combined with the word form variants of bigrams, trigrams and both.
-The best result without bag of lemmas comes from bag of words with only bigrams, with an F-score of $0.6376$, closely followed by bag of words with both types of $n$-grams, which got an F-score of $0.6337$.
-The best result overall came from the combination of bag of words, bag of lemmas, and both types of $n$-grams, which got an F-score of $0.6656$.
+We go on to test various combinations of these word form $n$-grams and the lexical \emph{bag-of} features.
+As seen in Table~\ref{tab:ngrams}, we test bag-of-words alone, and bag-of-words (BoW) with bag-of-lemmas (BoL), combined with the word form variants of bigrams, trigrams and both.
+The best result without BoL comes from BoW with only bigrams, with an F-score of $0.6376$, closely followed by BoW with both types of $n$-grams, which got an F-score of $0.6337$.
+However, the best result overall came from the combination of BoW, BoL, and both types of $n$-grams, which got an F-score of $0.6656$.
 
-Next, we add the different feature types.
-We use the bag-of feature template, and for each feature, test both the bag of features on its own, and with bag of words.
-As seen in Table \ref{tab:bagOfFeatures}, none of the feature types alone result in higher F-scores than bag of words.
-However, all feature types (except the lexicalized POS-tags), combined with bag of words, perform better than bag of words alone.
-Though none of them beat bag of words and lemmas combined, with an F-score of $0.6278$.
+Next, we include feature types based on the other information sources listed above, i.e., POS, dependencies, WordNet synsets, and Brown clusters.
+All these features are instantiated both with the \emph{bag-of} feature template on their own, and in combination with the bag-of-words features.
+As seen in Table~\ref{tab:bagOfFeatures}, none of the feature types alone yield higher F-scores than bag-of-words.
+On the other hand, when combined with BoW, all feature types (except the lexicalized POS-tags) perform better than BoW alone.
+However, none of them outperform BoW and BoL combined (F=$0.6278$, cf.
+Table~\ref{tab:ngrams}), or the combination of Bow+BoL with $n$-grams (F=$0.6656$).
 
@@
       Lemma backoff & $0.6611$ & $0.6480$ &  $\textbf{0.6649}$ \\ 
-      POS backoff & $\textbf{0.6410}$ & $0.6294$ & $0.6320$ \\
-      Dep backoff & $0.6208$ & $0.6194$ & $\textbf{0.6220}$ \\
-      Synset backoff & $0.6454$ & $0.6448$ &  $\textbf{0.6537}$\\
-      Brown backoff & $0.6285$ &  $0.6173$  & $\textbf{0.6335}$\\
+      POS backoff & $0.6410$ & $0.6294$ & $0.6320$ \\
+      Dep backoff & $0.6208$ & $0.6194$ & $0.6220$ \\
+      Synset backoff & $0.6454$ & $0.6448$ &  $0.6537$\\
+      Brown backoff & $0.6285$ &  $0.6173$  & $0.6335$\\
 
@@
 
-Next, we combine the results of bag of features, and $n$-grams, with $n$-gram feature backoffs.
-In Table \ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the results without backoff features.
+Next, the $n$-grams and \emph{bag-of} features are combined with generalized versions of $n$-gram features using the `backoff' strategy described in the previous section.
+In Table~\ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the results without backoff features.
 We test all possible backoff combinations.
+% fixme: forklar mer eksplisitt hvilke trekk som inngår i modellene i tabell 5, jeg klarte ikke gjøre rede for det selv.
 
@@
       \toprule           
-      Dependency backoff & Simple & Combined\\
+      Dependency backoff & BoW+dep & All\\
       \midrule
@@
   \end{center}
-  \caption{Dependency triples with and without feature backoff.
-Simple is the feature set containing bag of words and dependency triples.
-Combined is the feature set containing bag of words, bag of lemmas, bigrams, trigrams and dependency triples.
+  \caption{Dependency triples with and without feature backoff, in combination with other features: 
+`BoW+dep' is the feature set containing bag-of-words and dependency triples.
+`All' is the feature set containing BoW, BoL, bi- and trigrams and dependency triples.
 Each row backs off to a different feature type.}
@@
 As with $n$-gram backoff, we test multiple variations of backoff, both head-backoff and modifier-backoff.
-The results reported are the backoff variant that acheived the best results.
+The results reported are the backoff variant that achieved the best results.
 As seen in Table \ref{tab:depbackoff}, the inclusion of word form dependency triples improved upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for bag of words alone.
@@
 
-Our final model (which we refer to as ``Combined'') is the model consisting of bag of word forms, bag of lemmas, and word form bigrams and trigrams, which got the best result, with an F-score of $0.6656$.
-In Subsection \ref{sec:heldout} we will also test that same model with the addition of trigram backoff to lemmas, which got an F-score of $0.6649$.
+For the development data, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$.
+We will refer to this model as `lexical $n$-grams', and in the next section we present a brief error analysis before moving on to held-out testing.
+
+ % In Section~\ref{sec:heldout} we will also test that same model with the addition of trigram backoff to lemmas, which got an F-score of $0.6649$.
 
@@
 %% Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set. 
-The combined feature set acheived a precision of $0.7709$, and a recall of $0.5857$.
-Compared with our baseline system, which had a precision of $0.6777$, and a recall of $0.5585$, we see that the majority of the improvement over the baseline comes from the increase in precision.
-When reviewing a random subsample of the false positives and false negatives, we see that the noisy data has caused some problems for the preprocessor.
-Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context.
+The lexical $n$-gram feature set achieved a precision (P) of $0.7709$ and a recall (R) of $0.5857$.
+Compared with our initial BoW system, which had P=$0.6777$ and R=$0.5585$, we see that the majority of the improvement comes from the increase in precision.
+When reviewing a random sub-sample of the false positives and false negatives, we see that the noisy data has caused some problems for the pre-processor.
+% fixme: kanskje forklare mer hva det siktes til her?
+Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context. % fixme: gi eksempler på fenomener vi sikter til her?
 
@@
 
-We performed our final testing on the held-out test set using the baseline feature set, the combined feature set, and the combined features set with trigram backoff using lemma features.
-As seen in Table \ref{tab:heldout}, both the best feature set, and the second best, from our development testing, outperformed the baseline feature set.
-The best feature set from development also outperformed the second best.
-The difference in F-scores between the baseline and the best feature set was not as large as in our development testing.
-However, this may be due to the fact that the baseline performed a lot better in the held-out testing compared to the development testing, with an F-score of $0.6562$.
+We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model.
+As seen in Table~\ref{tab:heldout}, the $n$-gram model outperforms the BoW model by a good margin, with F-scores of $0.6860$ and $0.6562$ respectively.
+However, the difference in F-scores between the two feature sets is not as large as on the development data.
+At the same time, we see that both models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$).
+% fixme: noen teori om hvorfor vi ser denne effekten?
+% fixme: si noe som størrelsen på held-out dataene.
+
+% fixme: sier vi noe sted eksplisitt om testing skjer på setningsnivå eller kommentarnivå?
+
+% However, this may be due to the fact that the basic BoW model performed a lot better in the held-out testing compared to the development testing, with an F-score of $0.6562$.
 The F-scores of the combined feature sets were $0.6860$ and $0.6799$.
@@
       Combined & $0.7532$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
-      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            
+%      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            
       \bottomrule
@@
   \end{center}
-  \caption{Precision, recall and F-score for the baseline feature set, the best feature set, and the best backoff feature set, when classification is performed on the held-out test set.}
+  \caption{Precision, recall and F-score on the held-out test set for the basic BoW model and the best development feature set; the lexical $n$-gram model.}
   \label{tab:heldout}
@@
 
+This paper has developed and compared several machine-learned models for automatically detecting threats of violence in online discussions.
+The data set comprises a manually annotated corpus of comments from YouTube videos.
+We have reported experimental results for different classification frameworks and a wide range of different linguistic features.
+The best performance was observed for combinations of simple lexical features (bag-of-words- and lemmas, in combination with bi- and trigrams).
+Introducing more complex features -- drawing on information from WordNet synsets, Brown clusters, POS tags and dependency parses -- did not improve on the simpler surface-based feature set.
+
 \bibliography{wassa2016}

### 2016-04-01 submission.tex
mer krymping

@@
   \begin{itemize}[noitemsep]
-    \item Brown cluster label (100, 320, 1000 and 3200 clusters)
-    \item WordNet synset, parent synset and grandparent synset
+    \item Brown cluster label %(100, 320, 1000 and 3200 clusters)
+    \item WordNet synset, + parent and grandparent
   \end{itemize}
@@
 %% \end{description}
-The features are structured according to a set of \emph{feature templates}, which record varying degrees of linear order and syntactic context: \emph{bag-of} features (unordered), bigrams, trigrams and dependency triples.
-These feature templates are applied with the information sources presented above, yielding features like the following for our examples sentence in Figure~\ref{fig:dep}:
+The features are structured according to a set of \emph{feature templates},
+which record varying degrees of linear order and syntactic context:
+\emph{bag-of} features (unordered), bigrams, trigrams and dependency
+triples. Examples of the latter, given the sentence in Figure~\ref{fig:dep},
+would be: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, \ldots \}
 
-\begin{itemize}
-\setlength\itemsep{0em}
-\item Bigrams of word forms: \{i m,  m fucking, fucking scared, ...\}
-
-\item Dependency triples: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, ... \}
-\end{itemize}
-%<-- fixme: Hvis vi får plass kan vi kanskje legge til noen fler eksempler som bruker mer av den tilgjengelige informasjonen vi gjør et poeng av? F.eks n-grams av POS, synsets, lemma, osv?
+%These feature templates are applied with the information sources presented above, yielding features like the following for our examples sentence in Figure~\ref{fig:dep}:
+%% \begin{itemize}
+%% \setlength\itemsep{0em}
+%% \item Bigrams of word forms: \{i m,  m fucking, fucking scared, ...\}
+%%%
+%% \item Dependency triples: \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, ... \}
+%% \end{itemize}
 
@@
         \midrule
-        Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
-        Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
+        Bag-of-words & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
+        Bag-of-lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
         Bigrams of word forms & $0.4856$ & $0.4887$ & $0.4944$ \\
@@
 
-Table~\ref{tab:baseline} shows initial development results in terms of F-score for the the three different classifiers across four different feature sets; bags of word-forms and lemmas, as well as bigram and trigram over word forms.
+Table~\ref{tab:baseline} shows initial development results in terms of F-score for the the three different classifiers across four different feature sets; bags of word-forms and lemmas, as well as bigrams and trigrams over word forms.
 Generally, we see that feature sets containing lexical \emph{bag-of} features outperform the $n$-gram features.
@@
   \end{center}
-  \caption{F-scores of bag of features (BoF) with and without bag of words (BoW).
+  \caption{F-scores of \emph{bag-of} features (BoF) with and without bag-of-words (BoW).
 POS\textsubscript{Lex} and Dep\textsubscript{Lex} are lexicalized POS and dep-tags, respectively, where each feature is a tuple consisting of the tag and the word form of the token.}
@@
   \end{center}
-  \caption{Backoff from different combinations of $n$-grams. The models also contain bag of words, and bag of features. Each backoff combination is the one that achieved the best result.}
+  \caption{Backoff from different combinations of $n$-grams. The models also
+    contain bag-of-words and the other \emph{bag-of} features. Each backoff combination is the one that achieved the best result.}
   \label{tab:ngrambackoff}
@@
 
-Lastly, we will test the addition of dependency triples to our models.
-We add dependency triples consisting of word forms, both alone, and in conjunction with feature backoffs.
-As with $n$-gram backoff, we test multiple variations of backoff, both head-backoff and modifier-backoff.
-The results reported are the backoff variant that achieved the best results.
-As seen in Table \ref{tab:depbackoff}, the inclusion of word form dependency triples improved upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for bag of words alone.
-Dependency triples did not, however, improve upon the results achieved by our best model, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
-
-The addition of backoff also did not improve upon our best model.
-Adding POS backoff to our simplest model resulted in a slightly increased F-score of $0.6298$.
-Adding backoff to our combined model, however, only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.
+Lastly, we will test the addition of dependency triples to our models. We add
+dependency triples consisting of word forms, both alone, and in conjunction
+with feature backoffs. As with $n$-gram backoff, we test multiple variations of
+backoff, both head-backoff and modifier-backoff. The results reported are the
+backoff variant that achieved the best results. As seen in Table
+\ref{tab:depbackoff}, the inclusion of word form dependency triples improved
+upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for
+bag-of-words alone. Dependency triples did not, however, improve upon the
+results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
+Neither did the addition of backoff improve upon this model. Adding POS backoff
+to the `BoW+dep' configuration resulted in a slightly increased F-score of
+$0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.
 
 For the development data, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$.
-We will refer to this model as `lexical $n$-grams', and in the next section we present a brief error analysis before moving on to held-out testing.
+We will refer to this model as `lexical $n$-grams'.
+% and in the next section we present a brief error analysis before moving on to held-out testing.
 
@@
 
-\subsection{Error analysis}
+%\subsection{Error analysis}
 
@@
 % fixme: kanskje forklare mer hva det siktes til her?
-Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context. % fixme: gi eksempler på fenomener vi sikter til her?
+Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context.
+
+% fixme: gi eksempler på fenomener vi sikter til her?
 
@@
       \midrule
-      Baseline & $0.7325$ & $0.5943$ & $0.6562$ \\
-      Combined & $0.7532$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
+      BoW & $0.7325$ & $0.5943$ & $0.6562$ \\
+      Combined & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
 %      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            

### 2016-04-01 submission.tex
oppdatert modellnavn

@@
 results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
-Neither did the addition of backoff improve upon this model. Adding POS backoff
+Neither did the addition of backoff improve upon this. Adding POS backoff
 to the `BoW+dep' configuration resulted in a slightly increased F-score of
@@
 
-For the development data, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$.
+For the development data then, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$.
 We will refer to this model as `lexical $n$-grams'.
-% and in the next section we present a brief error analysis before moving on to held-out testing.
+% fixme: burde kanskje ha introdusert denne termen tidligere?
 
@@
       BoW & $0.7325$ & $0.5943$ & $0.6562$ \\
-      Combined & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
+      Lexical $n$-grams & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
 %      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            

### 2016-04-02 submission.tex
Added significance testing and SVM held-out result

@@
 The best results were obtained using only unigram features, with a precision of 0.67 and a recall of 0.60.
-The other feature sets garnered much lower results, and the authors suggest that deeper parsing could reveal significant phrase patterns.
+%% The other feature sets garnered much lower results, and
+The authors suggest that deeper parsing could reveal significant phrase patterns.
 % only unigrams best results
@@
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
-When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set).
-In the following experiments, we perform tuning on all feature sets.
+When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree %% (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model)
+, and the number of trees %% (10, 100 or 1000, depending on the size of the feature set)
+. In the following experiments, we perform tuning on all feature sets.
 
@@
 We will also only be using the the MaxEnt classifier for the remainder for reported development experiments.
-Not only did the MaxEnt model have the best performance for the basic BoW feature sets, but it is also the framework that is most convenient to use for exploring many combinations of features given that a MaxEnt model can be trained in much less time than an SVM or Random Forest classifier.
+Besides acheiving the best result on the BoW feature set, MaxEnt also has a shorter training time than the other two classifiers.%% Not only did the MaxEnt model have the best performance for the basic BoW feature sets, but it is also the framework that is most convenient to use for exploring many combinations of features given that a MaxEnt model can be trained in much less time than an SVM or Random Forest classifier.
 
@@
 dependency triples consisting of word forms, both alone, and in conjunction
-with feature backoffs. As with $n$-gram backoff, we test multiple variations of
-backoff, both head-backoff and modifier-backoff. The results reported are the
-backoff variant that achieved the best results. As seen in Table
+with feature backoffs. We test both head-backoff and modifier-backoff, and we report the variant that achieved the best results. As seen in Table
 \ref{tab:depbackoff}, the inclusion of word form dependency triples improved
@@
 results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
-Neither did the addition of backoff improve upon this. Adding POS backoff
-to the `BoW+dep' configuration resulted in a slightly increased F-score of
-$0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.
+The addition of backoff also did not improve the results above the previous best performer.
+%% Neither did the addition of backoff improve upon this. Adding POS backoff
+%% to the `BoW+dep' configuration resulted in a slightly increased F-score of
+%% $0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.
 
@@
 The lexical $n$-gram feature set achieved a precision (P) of $0.7709$ and a recall (R) of $0.5857$.
+The performance of the same feature set improved slightly when using the SVM classifier (F=$0.6667$, P=$0.7629$, R=$0.5920$).
 Compared with our initial BoW system, which had P=$0.6777$ and R=$0.5585$, we see that the majority of the improvement comes from the increase in precision.
+Both increases are statistically significant, with p-values of $1.3\mathrm{e}{-11}$ and $8.6\mathrm{e}{-11}$ for the lexical $n$-gram system using MaxEnt and SVM, respectively, when comparing with BoW, using the Wilcoxon significance test.
 When reviewing a random sub-sample of the false positives and false negatives, we see that the noisy data has caused some problems for the pre-processor.
@@
 We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model.
+The held-out test set consists of 5,685 sentences, 281 of which are threats, and we train on the entire development set.
 As seen in Table~\ref{tab:heldout}, the $n$-gram model outperforms the BoW model by a good margin, with F-scores of $0.6860$ and $0.6562$ respectively.
-However, the difference in F-scores between the two feature sets is not as large as on the development data.
-At the same time, we see that both models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$).
+However, the difference in F-scores between the two feature sets is not as large as on the development data, and they are in fact not statistically significant, with p-values of $0.14$ and $0.16$, when comparing the MaxEnt and SVM lexical n-gram models, respectivley, to BoW, using Wilcoxon.
+At the same time, we see that all the models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$).
 % fixme: noen teori om hvorfor vi ser denne effekten?
-% fixme: si noe som størrelsen på held-out dataene.
+% fixedfixme: si noe som størrelsen på held-out dataene.
 
@@
       BoW & $0.7325$ & $0.5943$ & $0.6562$ \\
-      Lexical $n$-grams & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
+      Lexical $n$-grams, MaxEnt & $\textbf{0.7532}$ & $0.6299$ & $0.6860$  \\
+
+      Lexical $n$-grams, SVM & $0.7490$ & $\textbf{0.6370}$ & $\textbf{0.6885}$  \\
 %      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            

### 2016-04-02 submission.tex
Finished the significance and held-out portions

@@
 After 6 iterations, we terminate the tuning, and select the best performing C-value.
-When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree %% (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model)
-, and the number of trees %% (10, 100 or 1000, depending on the size of the feature set)
-. In the following experiments, we perform tuning on all feature sets.
+When tuning the Random Forest classifier, we perform a grid search over the number of trees, and the maximum number of features used when splitting a node in the tree.
+%% (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model)
+%% , and the number of trees 
+%% (10, 100 or 1000, depending on the size of the feature set)
+In the following experiments, we perform tuning on all feature sets.
 
@@
 However, none of them outperform BoW and BoL combined (F=$0.6278$, cf.
-Table~\ref{tab:ngrams}), or the combination of Bow+BoL with $n$-grams (F=$0.6656$).
+Table~\ref{tab:ngrams}), or the combination of BoW+BoL with $n$-grams (F=$0.6656$).
 
@@
   \caption{Backoff from different combinations of $n$-grams. The models also
-    contain bag-of-words and the other \emph{bag-of} features. Each backoff combination is the one that achieved the best result.}
+    contain bag-of-words, and BoF for each feature, as in Table \ref{tab:bagOfFeatures}. Each backoff combination is the one that achieved the best result.}
   \label{tab:ngrambackoff}
@@
 We test all possible backoff combinations.
-% fixme: forklar mer eksplisitt hvilke trekk som inngår i modellene i tabell 5, jeg klarte ikke gjøre rede for det selv.
+% fixed fixme: forklar mer eksplisitt hvilke trekk som inngår i modellene i tabell 5, jeg klarte ikke gjøre rede for det selv.
 
@@
 bag-of-words alone. Dependency triples did not, however, improve upon the
-results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
+results achieved by our previous best performer (F=$0.6656$). %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
 The addition of backoff also did not improve the results above the previous best performer.
@@
 We will refer to this model as `lexical $n$-grams'.
-% fixme: burde kanskje ha introdusert denne termen tidligere?
+% fixed fixme: burde kanskje ha introdusert denne termen tidligere?
+Aksel: Jeg syns ikke det
 
@@
 Compared with our initial BoW system, which had P=$0.6777$ and R=$0.5585$, we see that the majority of the improvement comes from the increase in precision.
-Both increases are statistically significant, with p-values of $1.3\mathrm{e}{-11}$ and $8.6\mathrm{e}{-11}$ for the lexical $n$-gram system using MaxEnt and SVM, respectively, when comparing with BoW, using the Wilcoxon significance test.
+The increases in both models compared with BoW are statistically significant, with p-values of $1.3\mathrm{e}{-11}$ and $8.6\mathrm{e}{-11}$ for the lexical $n$-gram system using MaxEnt and SVM, respectively, using the Wilcoxon signed-rank test.
 When reviewing a random sub-sample of the false positives and false negatives, we see that the noisy data has caused some problems for the pre-processor.
@@
 
-We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model.
+We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model, using both the MaxEnt and SVM classifiers.
 The held-out test set consists of 5,685 sentences, 281 of which are threats, and we train on the entire development set.
-As seen in Table~\ref{tab:heldout}, the $n$-gram model outperforms the BoW model by a good margin, with F-scores of $0.6860$ and $0.6562$ respectively.
-However, the difference in F-scores between the two feature sets is not as large as on the development data, and they are in fact not statistically significant, with p-values of $0.14$ and $0.16$, when comparing the MaxEnt and SVM lexical n-gram models, respectivley, to BoW, using Wilcoxon.
+As seen in Table~\ref{tab:heldout}, the $n$-gram models outperforms the BoW model by a good margin, with F-scores of $0.6885$ (SVM), $0.6860$ (MaxEnt), and $0.6562$ (BoW).
+However, the difference in F-scores between the two feature sets is not as large as on the development data, and they are in fact not statistically significant, with p-values of $0.14$ and $0.16$, when comparing the MaxEnt and SVM lexical n-gram models, respectively, to BoW, using Wilcoxon.
 At the same time, we see that all the models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$).
 % fixme: noen teori om hvorfor vi ser denne effekten?
-% fixedfixme: si noe som størrelsen på held-out dataene.
+% fixed fixme: si noe som størrelsen på held-out dataene.
 

### 2016-05-03 submission.tex
updated author list

@@
 
+%\clubsuit
+
 % Author information can be set in various styles:
 % For several authors from the same institution:
-\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
-  Department of Informatics \\
-  University of Oslo, Norway \\
-  \{aksellw, liljao, erikve\}@ifi.uio.no}
+%\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
+%  Department of Informatics \\
+%  University of Oslo, Norway \\
+%  \{aksellw, liljao, erikve\}@ifi.uio.no}
+% if the names do not fit well on one line use
+
+% Author information can be set in various styles:
+% For several authors from the same institution:
+\author{Aksel Wester$^1$ \and Lilja Øvrelid$^1$ \and Erik Velldal$^1$ \and Hugo Lewi Hammer$^2$\\[1ex]
+  ${}^1$ Department of Informatics\\ University of Oslo\\
+  {\smaller {\tt \{aksellw, liljao, erikve\}@ifi.uio.no}}\\[1ex]
+${}^2$ Department of Computer Science\\ Oslo and Akershus University College of Applied Sciences\\
+{\smaller{\tt hugo.hammer@hioa.no}}}
 % if the names do not fit well on one line use
